\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

{\color{linkedinblue}
\noindent [Company Name] \\
Hiring Manager \\
[Contact Email] \\
[Address] \\
[City], Sweden
}

\vspace{2cm}

Hej,

\vspace{0.5cm}

I am excited to apply for the [Position] position at [Company Name]. As a backend developer with a unique background bridging business and technology, I bring not just Java/Spring Boot expertise, but the ability to understand business workflows and translate them into robust, data-driven backend solutions.

My experience spans backend development and cross-cultural collaboration. At Senior Material (Europe) AB, I led the migration from monolith to containerized microservices architecture, working closely with business stakeholders to ensure the new system met manufacturing workflow requirements. At IT-Högskolan, I worked on the "Omstallningsstod.se" platform backend with Spring Boot, ensuring API compatibility while collaborating with distributed international teams.

What sets me apart is my ability to bridge technical and business worlds. My Master's in International Business, combined with Bachelor's degrees in both Java Integration and .NET Cloud Development, means I understand how backend architecture decisions affect operational efficiency, maintenance costs, and business scalability. This cross-cultural communication ability and business-IT integration mindset enable me to analyze complex problems, understand real customer needs, and propose effective technical solutions.

Beyond my professional work, I build practical systems driven by real business demands. I created the AI Math Grader—a K-12 grading system with Spring Boot backend that addresses teachers' actual workflow needs for instant, pedagogical feedback. I also developed an Invoice Handling System using AI to streamline financial processes—spotting a real business pain point and solving it with a smooth, data-driven backend solution. These projects demonstrate my ability to identify business demands and architect practical technical solutions.

I'm fluent in English and Mandarin Chinese, with Swedish B2 proficiency, enabling seamless collaboration in multicultural environments. My testing advocacy (TDD, JUnit, Mockito) and maintenance mindset ensure I build systems that are not just functional, but maintainable and scalable. I would love to discuss how my backend expertise, cross-cultural communication skills, and business-IT integration mindset can contribute to [Company Name]'s continued success.

\vspace{0.5cm}

Sincerely, \\
Harvad (Hongzhi) Li

\vspace{2cm}

{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

\noindent Gårdsvägen 9 \\
431 38 Mölndal, Sweden \\
hongzhili01@gmail.com \\
+46 72 838 4299

\end{document}
