\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (no name)
\begin{center}
{\Large \textbf{COMPANY\_NAME}}\\[4pt]
{\Large \textbf{JOB\_TITLE}}\\[4pt]
{\Large \textbf{Gothenburg, Sweden}}\\[8pt]
\end{center}

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}
I'm excited to apply for the Incident Management Specialist position at Tata Technologies. With 5+ years managing production infrastructure, resolving critical incidents, and optimizing cloud operations, I'm confident I can contribute immediately to your Cloud \& Connectivity team.

\textbf{Incident Management Expertise:} At ECARX, I provide 24/7 on-call support across 4 global offices (Gothenburg, London, Stuttgart, San Diego). My most significant achievement was resolving a critical incident affecting 26 servers at H3C's largest Swedish customer (Zeekr) - I performed systematic root cause analysis under pressure, identified outdated configuration files causing cyclic crashes, and completed remediation within 5 hours. This experience demonstrates my ability to work under pressure, perform thorough RCA, and restore production systems rapidly.

\textbf{Infrastructure \& Automation:} I led the migration from Azure AKS to on-premise Kubernetes, reducing cloud costs by 45\% while improving CI/CD efficiency by 25\%. I deployed comprehensive Prometheus/Grafana monitoring stacks that reduced MTTR by 35\% through proactive alerting. I automate infrastructure using Terraform and Ansible, reducing manual intervention by 60\% and accelerating release cycles.

\textbf{Technical Alignment:} My skills directly match your requirements - AWS/Azure certified with hands-on experience in EC2, S3, Lambda, AKS; expert in Terraform and CloudFormation for IaC; proficient with Jenkins, GitHub Actions, and GitLab CI for CI/CD; deep expertise in Prometheus, Grafana, and ELK for observability; strong Python and Bash scripting for automation; production Kubernetes experience including troubleshooting and optimization.

\textbf{Why Tata Technologies:} I'm drawn to your focus on digital transformation for world-leading manufacturers. As a Gothenburg resident with Swedish permanent residence, I'm immediately available and excited about working on-site. My experience with international teams (English/Swedish/Chinese fluency) and Agile methodologies positions me well for your global environment.

I'm passionate about platform reliability, MTTR reduction, and developer experience improvements. I'd welcome the opportunity to discuss how my incident management expertise and infrastructure automation skills can contribute to Tata Technologies' success. Thank you for considering my application.
\vspace{1cm}

Best Regards,\\[0.5cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date
\noindent Ebbe Lieberathsgatan 27, 41265 Gothenburg, Sweden \hfill \today

\end{document}