\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{parskip}

% Page setup
\geometry{margin=1in}
\pagestyle{empty}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

\begin{document}

% Header
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[5pt]
\textcolor{darkblue}{Junior Software Engineer | C\# & React Specialist}\\[5pt]
\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | Gothenburg, Sweden
\end{center}

\vspace{20pt}

\today

\vspace{10pt}

\textbf{Kollmorgen Automation AB}\\
Mölndal, Sweden

\vspace{20pt}

\textbf{Re: Application for Junior Software Engineer}

\vspace{10pt}

Dear Hiring Team,

I am writing to apply for the Junior Software Engineer position at Kollmorgen. Having reviewed your requirements for a candidate with a strong educational background in IT and hands-on knowledge of **React, Typescript, C#, and .NET**, I am confident that my profile is a direct match for this role.

My Bachelor's degree in .NET Cloud Development provided me with intensive training in the exact stack you utilize. I have applied this knowledge to build software solutions using **C# and .NET**, ensuring clean, maintainable code. For example, my "Crypto Wallet" project was built entirely within the .NET ecosystem, challenging me to implement secure, efficient logic using C#.

On the frontend, I possess the required hands-on knowledge of **React and Typescript**. I have developed responsive user interfaces that prioritize user experience and performance, skills I am eager to apply to your web and cloud-based tools for AGV visualization.

I am also familiar with **Azure**, having used it for application deployment and CI/CD pipeline management during my studies and freelance work. I understand the importance of cloud solutions in modern automation and am excited about the opportunity to work with Azure in a professional setting at Kollmorgen.

I am a collaborative team player who is fluent in English and eager to learn. I am passionate about joining a company like Kollmorgen that is a leader in AGV and AMR technology, and I am ready to contribute to your Engineering department from day one.

Thank you for your time and consideration.

Sincerely,

Harvad (Hongzhi) Li

\end{document}
