\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}

% Page setup
\geometry{margin=0.75in}
\pagestyle{empty}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{lightgray}{RGB}{128,128,128}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue
}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

% Custom commands
\newcommand{\contactitem}[2]{\textcolor{darkblue}{#1} #2}

\begin{document}
\pagestyle{empty} % no page number

% Name and contact details
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[10pt]
{\Large \textit{Junior Software Engineer | C\#, .NET & React Specialist}}\\[10pt]
\textcolor{darkblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}

% Personal Profile
\section*{Profile Summary}
Aspiring Junior Software Engineer with a dedicated focus on the Microsoft technology stack and modern web development. Holding a Bachelor's degree in .NET Cloud Development, I have built a strong foundation in \textbf{C\#, .NET, React, and TypeScript}. I am passionate about creating efficient, maintainable software and am eager to apply my skills in \textbf{Azure} cloud solutions to the exciting field of AGV and AMR automation at Kollmorgen. I thrive in collaborative environments and am committed to continuous learning and high code quality.

% Areas of Expertise
\section*{Core Technical Skills}
\begin{itemize}[noitemsep]
\item \textbf{Primary Languages:} C\#, TypeScript
\item \textbf{Frameworks & Libraries:} .NET (Core/5+), React
\item \textbf{Cloud & Tools:} Azure, Git
\item \textbf{Languages:} Fluent English (Spoken & Written)
\end{itemize}

% Experience
\section*{Working Experience}
\subsection*{Synteda | Software Developer (Freelance)}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Developed software solutions using \textbf{C\#} and \textbf{.NET} technologies.
\item Implemented responsive user interfaces with \textbf{React} and \textbf{TypeScript}.
\item Utilized \textbf{Azure} for cloud-based application deployment and management.
\end{itemize}

\subsection*{IT-Högskolan | DevOps Support (Part-time)}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Supported development teams working with \textbf{.NET} ecosystems.
\item Assisted in setting up CI/CD pipelines within \textbf{Azure DevOps}.
\end{itemize}

\section*{Relevant Projects}

\subsection{Crypto\_Wallet\_Xamarin}
\textit{2024 -- Present} \\
\textbf{C\#, .NET, Mobile Development}
\begin{itemize}[noitemsep]
  \item Built a secure cryptocurrency wallet application using \textbf{C\#} and the \textbf{.NET} framework.
  \item Demonstrated strong understanding of object-oriented programming and state management in C\#.
\end{itemize}

\subsection{Gothenburg\_TaxiPooling}
\textit{May 2025 -- Present} \\
\textbf{TypeScript, React Native (React-based)}
\begin{itemize}[noitemsep]
  \item Developed a frontend application using \textbf{TypeScript} and React patterns.
  \item Focused on clean component architecture and efficient data handling.
\end{itemize}

\vspace{6pt}
\section*{Education}
\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Key Coursework: C#, .NET Core, Azure, Cloud Architecture}\\
\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textbf{University of Gothenburg} | Master's in International Business and Trade | 2016-2019

\vspace{6pt}
\section*{Certifications}
\begin{itemize}
\item Microsoft Certified: Azure Fundamentals (Jun 2022)
\end{itemize}

\end{document}
