\documentclass[a4paper,10pt]{letter}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{xcolor}\definecolor{darkblue}{rgb}{0.0,0.2,0.6}
\setlength{\parindent}{0pt}
\begin{document}\pagestyle{empty}
\begin{letter}{Essity\\Munich, Germany}
\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Cloud DevOps Engineer position at Essity. With over 4 years of hands\-on experience in cloud technologies, DevOps practices, and site reliability engineering across multinational organizations, I am excited about the opportunity to contribute to Essity's mission of improving quality of life through sustainable hygiene and health solutions.

My expertise spans Microsoft Azure (primary), AWS, and GCP, with proven experience in designing and managing multi\-cloud architectures. Currently serving as IT/Infrastructure Specialist at ECARX, I recently led a significant infrastructure optimization project migrating from Azure Kubernetes Service to on\-premises Kubernetes, achieving a 40\% reduction in operational costs. I deployed comprehensive monitoring using Prometheus and Grafana, and conducted detailed performance analysis that resulted in 25\% improvement in CI/CD pipeline execution times.

I have high expertise with the DevOps toolchains you require: Docker for containerization, Terraform for infrastructure as code, Azure DevOps for CI/CD pipelines, Git for version control, and Helm Charts for Kubernetes deployments. I have extensive experience in Azure DevOps CI/CD pipeline multi\-staging code deployment administration, implementing dev, staging, and production environments with automated testing, security scanning, and zero\-downtime deployments using blue\-green strategies.

My software development background includes Python, C\#/.NET, and Go, which enables me to bridge the gap between development and operations effectively. I hold AWS Certified Solutions Architect Associate and AWS Certified Developer Associate certifications, demonstrating my commitment to professional excellence in cloud technologies.

What particularly resonates with me about Essity is your commitment to sustainability and the ``Business Ambition for 1.5 Degrees'' initiative. I am passionate about leveraging technology to create positive environmental impact, and I would be honored to contribute my DevOps and cloud expertise to help Essity achieve climate neutrality by 2050 while delivering high\-quality hygiene and health solutions with maximum resource efficiency.

I am eager to bring my DevOps expertise, cloud architecture knowledge, and passion for sustainable technology to Essity's team in Munich. Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to Essity's continued success.

\closing{Sincerely,}
\signature{Hongzhi Li\\Ebbe Lieberathsgatan 27\\412 65 G\"{o}teborg, Sweden\\hongzhili01@gmail.com\\+46 728 384 299\\2025.10.02}
\end{letter}\end{document}
