\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{rgb}{0.0, 0.2, 0.6}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}\\
Opera\\
Oslo, Norway}

\\
\vspace{40pt}

\opening{Hej,}

\vspace{10pt}

I am writing to express my sincere interest in the DevOps Engineer role at Opera. As an experienced DevOps professional with a unique combination of technical expertise and cross-cultural communication skills, I am excited about the opportunity to contribute to your team's success while bringing a fresh perspective to your infrastructure challenges.

What particularly excites me about Opera is the opportunity to work on innovative browser technology and contribute to products used by millions worldwide. My current role at ECARX has given me deep insights into complex system integration challenges, and I am passionate about leveraging my technical expertise to enhance user experiences through robust infrastructure solutions.

Throughout my career, I have excelled in cross-functional collaboration, serving as a bridge between development teams and infrastructure operations. My experience at ECARX has strengthened my ability to communicate complex technical concepts to both technical and non-technical stakeholders, ensuring seamless project delivery across diverse teams.

What sets me apart is my multicultural perspective and cross-cultural communication skills. Having worked across Swedish, Norwegian, and international business environments, I bring a unique ability to navigate cultural nuances while maintaining technical excellence. This has been particularly valuable when coordinating between IT departments and business units, translating business requirements into technical solutions.

My expertise extends beyond technical implementation to system integration and process optimization. At ECARX, I led the migration from AKS to local Kubernetes clusters while implementing comprehensive Prometheus and Grafana monitoring solutions. This project required not only technical skills but also extensive collaboration with multiple departments, change management, and stakeholder alignment, showcasing my ability to integrate complex systems while managing organizational change.

My technical foundation includes expertise in Kubernetes, Docker, AWS, Azure, Prometheus, Grafana, Python, and various CI/CD tools. However, what truly differentiates me is my ability to leverage these technical skills within a collaborative, multicultural context, ensuring that infrastructure solutions align with business objectives and user needs.

At Opera, I am particularly excited about the opportunity to contribute not just my technical skills, but also my experience in fostering collaboration, managing stakeholder relationships, and driving successful project outcomes through effective communication and integration practices.

I am confident that my combination of technical expertise, soft skills, and integration experience will make a valuable contribution to your team. I look forward to discussing how my unique background can support Opera's continued growth and success.

\vspace{20pt}

Sincerely,

Hongzhi Li\\
2025.08.12

\vspace{40pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}

\vspace{4pt}

\closing{\color{darkblue} 
Ebbe Lieberathsgatan 27\\
412 65 Göteborg\\
hongzhili01@gmail.com\\
0728384299}

\\
\vspace{10pt}

\end{letter}

\end{document}