\documentclass[a4paper,10pt]{letter}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{xcolor}\definecolor{darkblue}{rgb}{0.0,0.2,0.6}
\setlength{\parindent}{0pt}
\begin{document}\pagestyle{empty}
\begin{letter}{SKF Sweden AB\\von Utfallsgatan 2\\415 05 G\"{o}teborg}
\opening{Dear Hiring Manager,}

I am a full\-stack engineer with 5+ years building cloud applications across React/Angular frontends and Java/C\#/Python microservices backends. In the automotive domain, I work hands\-on with Android Auto and in\-vehicle experiences, while partnering across product, platform, and security to deliver compliant, high\-quality solutions.

My recent work centers on Azure and hybrid/multi\-cloud designs. I build with Azure App Services, Functions, Azure SQL and Azure DevOps, and I bring practical OCI and AWS experience for cross\-cloud interoperability. I set domain and sub\-domain policies, introduce CI/CD quality gates (build/test/scan), and collaborate with Cyber Security on identity, secrets, and policy\-as\-code so teams can move fast while meeting regulatory needs in multiple markets.

As a bridge between product, platform, and application teams in a multi\-national environment, I translate business outcomes into roadmaps and engineering constraints into business decisions. This reduces friction, improves alignment, and raises delivery quality. In Android Auto work, I deliver full\-stack features with reliable pipelines and testing (unit/integration/e2e) and use performance baselines to maintain a high bar.

I would be excited to bring this mix of full\-stack delivery, Azure/OCI pragmatism, and technical leadership to SKF in Gothenburg.

\closing{Sincerely,}
\signature{Hongzhi Li\\Ebbe Lieberathsgatan 27\\412 65 G\"{o}teborg\\hongzhili01@gmail.com\\0728384299\\2025.09.12}
\end{letter}\end{document}
