\documentclass[a4paper,10pt]{letter}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{xcolor}\definecolor{darkblue}{rgb}{0.0,0.2,0.6}
\setlength{\parindent}{0pt}
\begin{document}\pagestyle{empty}
\begin{letter}{Tata Technologies\\Gustaf Larsons v 15\\418 78 G\"{o}teborg}
\opening{Dear Hiring Manager,}

I am a cloud developer with 4+ years building event\-driven, secure distributed systems on AWS using .NET/C\#, Kubernetes (EKS), Terraform, MongoDB, Grafana, and Kafka. I integrate complex systems with a DevOps mindset—automation first, IaC everywhere, observable by default—and I focus on performance and reliability in production.

I enjoy the energy/sustainability domain. My recent projects include a Kafka\-based energy telemetry pipeline on EKS (IaC with Terraform, Grafana/Prometheus SLOs), a green fleet optimization service (.NET APIs on AWS with CI/CD and security scans), and Android Auto companion backends using event\-driven patterns and contract tests. I collaborate closely with security and platform teams on secrets, identity, and network policy to keep distributed systems safe and compliant.

I hold a valid B driver's license and have participated in vehicle testing and verification activities in Gothenburg, including programs for Polestar 5, EX30, and Hongqi. This hands\-on exposure to on\-road validation and test workflows informs how I design telemetry, observability, and safety\-critical integrations across cloud backends and in\-vehicle clients.

What motivates me is continuous improvement: tuning services for lower latency and better resource efficiency, strengthening pipelines with tests and policy gates, and using analytics to guide cost/performance trade\-offs. I communicate clearly, mentor others, and thrive in diverse teams that move fast while staying organized and structured.

I would be excited to bring this blend of .NET/AWS engineering, Kubernetes/IaC automation, and event\-driven design to Tata. Thank you for your time and consideration.

\closing{Sincerely,}
\signature{Hongzhi Li\\Ebbe Lieberathsgatan 27\\412 65 G\"{o}teborg\\hongzhili01@gmail.com\\+46 728 384 299\\2025.09.12}
\end{letter}\end{document}
