\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (no name) - Professional centered format
\begin{center}
{\Large \textbf{Omegapoint}}\\[4pt]
{\Large \textbf{Java Software Developer}}\\[4pt]
{\Large \textbf{Gothenburg, Sweden}}\\[8pt]
\end{center}

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}
I'm excited to apply for the Java Software Developer position at Omegapoint. As a backend developer with a unique background bridging business and technology, I bring not just Java/Spring Boot expertise, but the ability to understand business workflows and translate them into robust, data-driven solutions.

\textbf{Technical Expertise:} My experience spans backend development and cross-cultural collaboration. At Senior Material (Europe) AB, I led the migration from monolith to containerized microservices architecture. At IT-Högskolan, I worked on the "Omstallningsstod.se" platform backend with Spring Boot, collaborating with distributed international teams across different time zones.

\textbf{Business \& Technical Bridge:} What sets me apart is my ability to bridge technical and business worlds. My Master's in International Business, combined with Bachelor's degrees in both Java Integration and .NET Cloud Development, means I understand how backend architecture decisions affect operational efficiency and business scalability. This unique combination enables me to analyze complex problems, understand real customer needs, and propose effective technical solutions.

\textbf{Practical Innovation:} Beyond my professional work, I build practical systems driven by real business demands. I created the AI Math Grader—a K-12 grading system with Spring Boot backend that addresses teachers' actual workflow needs. I also developed an Invoice Handling System using AI to streamline financial processes—spotting a real business pain point and solving it with a smooth, data-driven backend solution. These projects demonstrate my testing advocacy (TDD, JUnit, Mockito) and maintenance mindset.

I'm fluent in English and Mandarin Chinese, with Swedish B2 proficiency. I would love to discuss how my backend expertise, cross-cultural communication skills, and business-IT integration mindset can contribute to Omegapoint's continued success.

Thank you for your time and consideration.

\vspace{1cm}

Sincerely,\\
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date only (no contact info)
\noindent Ebbe Lieberathsgatan 27\\
41265 Gothenburg, Sweden \hfill \today

\end{document}