\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{rgb}{0.0, 0.2, 0.6}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

{\color{darkblue}
Opera\\
Opera\\Gothenburg Office\\
411 XX Göteborg}

\vspace{40pt}

Hej,

\vspace{10pt}

I am writing to express my sincere interest in the DevOps Engineer role at Opera. As an experienced DevOps professional with deep expertise in cloud technologies and infrastructure automation, I am excited about the opportunity to contribute to Opera's technical excellence.

What draws me to Opera is your commitment to innovation and the opportunity to work with cutting-edge technologies in a collaborative environment. With my proven experience in designing and optimizing CI/CD pipelines across multiple cloud platforms, I am confident in my ability to streamline the software delivery processes for your mission-critical applications.

Throughout my career, I have consistently demonstrated a strong commitment to coaching cross-functional teams on modern development methodologies and fostering a culture of collaboration and continuous improvement. I thrive in multi-team environments, where I can leverage my overall understanding of complex systems and intricate integration processes to drive efficiency and innovation.
        
My multicultural background has equipped me with exceptional cross-cultural communication skills, having successfully worked across Swedish, Chinese, and international business environments. This unique perspective enables me to bridge communication gaps between technical teams and business stakeholders, ensuring that complex technical solutions align with business objectives and user needs.

At Opera, I am eager to contribute my skills and knowledge in tools such as Python, Git, Cloud/Azure, Kubernetes, Linux, Ansible, Terraform, PostgreSQL, Grafana, TypeScript, ReactJS, and Docker. My hands-on experience with these technologies, combined with my passion for delivering high-quality solutions, makes me an ideal candidate for this role.

I am impressed by Opera's commitment to innovation and technical excellence. As a proactive and results-driven professional, I welcome the opportunity to contribute to your team's success while growing professionally in this dynamic environment.

Thank you for considering my application. I look forward to discussing how my expertise and collaborative approach can contribute to Opera's continued success and innovation.

\vspace{20pt}

Sincerely,

Hongzhi Li\\
2025.08.15

\vspace{40pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}

\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg\\
hongzhili01@gmail.com\\
0728384299}

\end{document}