\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{margin=0.75in}
\setlength{\parindent}{0pt}
\definecolor{lightblue}{RGB}{0, 119, 181}
\hypersetup{colorlinks=true, linkcolor=lightblue, urlcolor=lightblue}

\begin{document}

% Header with job information (all in LinkedIn blue)
{\color{lightblue}\textbf{Volvo Group}}\\
{\color{lightblue}Full Stack Developer -- C\# / .NET (Infrastructure experience)}\\
{\color{lightblue}Gothenburg, Sweden}

\vspace{0.5cm}

Dear Lina,

\vspace{0.3cm}

I am writing to express my strong interest in the Full Stack Developer -- C\# / .NET position at Volvo Group. With over 6 years of experience building enterprise applications using C\#, ASP.NET Core, Azure cloud-native technologies, and Infrastructure as Code, combined with my automotive industry experience at ECARX supporting Volvo Cars and Polestar, I am confident I can contribute immediately to your team developing business-critical systems for part number setup and lifecycle management.

\vspace{0.3cm}

\textbf{Full-Stack .NET \& Infrastructure Expertise:}

\begin{itemize}[noitemsep,leftmargin=*,topsep=0pt]
\item \textbf{C\# / .NET Mastery:} 6+ years building production applications with ASP.NET Core, Entity Framework Core, and REST APIs. Experienced with microservices architecture, domain-driven design, and event-driven patterns
\item \textbf{Frontend Development:} Hands-on experience with Angular, Blazor (Server \& WebAssembly), and React/TypeScript for building modern SPA applications with responsive UI/UX
\item \textbf{Database Expertise:} Proficient in SQL Server, PostgreSQL, and Azure Cosmos DB. Strong skills in database design, query optimization, and Entity Framework Core migrations
\item \textbf{Azure Cloud-Native:} Extensive experience with Kubernetes (AKS), Azure Red Hat OpenShift exposure, Docker containerization, and Azure services (Key Vault, API Management, Entra ID)
\item \textbf{Infrastructure as Code:} Deep expertise in Terraform for provisioning and maintaining Azure environments. Implemented IaC best practices reducing manual infrastructure tasks by 60\%
\item \textbf{CI/CD \& GitOps:} Built automated pipelines with Azure DevOps, GitHub Actions, and Argo CD. Strong advocate for GitOps workflows and declarative deployments
\end{itemize}

\vspace{0.3cm}

\textbf{Automotive Industry \& DevOps Culture:}

At ECARX, I worked directly with Volvo Cars, Polestar, Lynk\&Co, and Geely, gaining deep understanding of automotive environment requirements. I led Azure infrastructure optimization achieving 35\% cost reduction while maintaining performance, managed Kubernetes migrations with zero downtime, and championed DevOps practices including continuous improvement and AI-assisted development tools (GitHub Copilot, Cursor AI). My experience spans the full stack from backend microservices to frontend SPAs, with strong focus on cloud-native architecture and infrastructure automation.

\vspace{0.3cm}

\textbf{Proactive, Collaborative, \& Adaptable:}

I thrive in high-delivery agile teams and take ownership from development through deployment. My approach combines curiosity with continuous-improvement mindset, actively seeking better solutions and adopting new technologies. At Synteda, I led the Mibo.se digital transformation from simple website to MS-integrated office system, demonstrating ability to deliver complex solutions in collaborative team environment. I'm passionate about responsible AI adoption in engineering and platform work, having successfully integrated AI-assisted development tools to improve productivity and code quality.

\vspace{0.3cm}

I am particularly drawn to Volvo Group because of your leadership in automotive innovation and commitment to technical excellence. My combination of full-stack .NET expertise, infrastructure experience, automotive industry knowledge, and DevOps mindset makes me well-suited for this role. I'm excited about the opportunity to contribute to business-critical systems supporting product configuration, manufacturing, and enterprise integrations.

\vspace{0.3cm}

I would welcome the opportunity to discuss how my experience can contribute to your team's success. Thank you for considering my application.

\vspace{0.5cm}

Best Regards,\\[0.3cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator (LinkedIn blue)
{\color{lightblue}\hrule height 0.5pt}

\vspace{0.2cm}

% Footer with address and date (all in LinkedIn blue, 3 lines, left-aligned like header)
{\color{lightblue}Ebbe Lieberathsgatan 27}\\
{\color{lightblue}412 65, Gothenburg, Sweden}\\
{\color{lightblue}\today}

\end{document}
