\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\signature{Your Full Name}
\address{Your Full Name \\ Gothenburg, Sweden \\ +46 70 123 4567 \\ your.email@example.com}

\begin{document}

\begin{letter}{Hiring Manager \\ Spotify Technology \\ Stockholm, Sweden}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Senior Backend Developer position at Spotify Technology. With my solid background in Python development and passion for building scalable software solutions, I am confident I would make a valuable contribution to your development team.

I am excited about Spotify's mission to unlock human creativity through music and audio. Your innovative approach to streaming technology and data-driven personalization represents the kind of impactful work I want to contribute to.

In my current role as Software Developer, I have built extensive expertise in Python, FastAPI, and PostgreSQL, which aligns well with your technical requirements. I have successfully developed and maintained microservices architectures serving over 100,000 daily users and implemented CI/CD pipelines that improved deployment efficiency by 60\%.

My experience leading development projects and mentoring team members has prepared me well for the senior-level responsibilities of this role. My experience includes:

\begin{itemize}
\item 5+ years of Python development with modern frameworks (FastAPI, Django)
\item Proven experience building scalable backend systems and RESTful APIs
\item Strong database design skills with PostgreSQL and performance optimization
\item Hands-on experience with Docker, Kubernetes, and cloud deployment
\item Experience working in agile development environments with cross-functional teams
\end{itemize}

What particularly excites me about this opportunity is the chance to work on challenging technical problems and contribute to Spotify Technology's continued innovation. My problem-solving approach, attention to code quality, and collaborative mindset make me well-suited for your team's dynamic environment.

I would welcome the opportunity to discuss how my technical skills and experience can contribute to Spotify Technology's success. Thank you for your time and consideration.

\closing{Best regards,}

\end{letter}
\end{document}