\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\signature{Your Full Name}
\address{Your Full Name \\ Gothenburg, Sweden \\ +46 70 123 4567 \\ your.email@example.com}

\begin{document}

\begin{letter}{Hiring Manager \\ CEVT (China Euro Vehicle Technology) \\ Gothenburg, Sweden}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Data Engineer position at CEVT (China Euro Vehicle Technology). With my solid background in Python development and passion for building scalable software solutions, I am confident I would make a valuable contribution to your development team.

I am impressed by CEVT (China Euro Vehicle Technology)'s reputation for technical excellence and innovation. Your commitment to delivering high-quality solutions aligns with my professional values and technical standards.

In my current role as Software Developer, I have built extensive expertise in Python, FastAPI, and PostgreSQL, which aligns well with your technical requirements. I have successfully developed and maintained microservices architectures serving over 100,000 daily users and implemented CI/CD pipelines that improved deployment efficiency by 60\%.

My strong technical background in Python and backend development directly matches the requirements for this position. My experience includes:

\begin{itemize}
\item 5+ years of Python development with modern frameworks (FastAPI, Django)
\item Proven experience building scalable backend systems and RESTful APIs
\item Strong database design skills with PostgreSQL and performance optimization
\item Hands-on experience with Docker, Kubernetes, and cloud deployment
\item Knowledge of automotive industry standards and embedded systems
\end{itemize}

What particularly excites me about this opportunity is the chance to work on challenging technical problems and contribute to CEVT (China Euro Vehicle Technology)'s continued innovation. My problem-solving approach, attention to code quality, and collaborative mindset make me well-suited for your team's dynamic environment.

I would welcome the opportunity to discuss how my technical skills and experience can contribute to CEVT (China Euro Vehicle Technology)'s success. Thank you for your time and consideration.

\closing{Best regards,}

\end{letter}
\end{document}