\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=0.75in}
\pagestyle{empty}

\definecolor{darkblue}{RGB}{0,51,102}

\hypersetup{colorlinks=true, linkcolor=darkblue, urlcolor=darkblue}

\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

\begin{document}
\pagestyle{empty}

\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[10pt]
{\Large Fullstack Developer | Software Quality \& Testing Specialist}\\[10pt]
\textcolor{darkblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}

\section*{Profile Summary}

Quality-driven \textbf{Fullstack Developer} with over 4 years of experience, specializing in the \textbf{.NET 8 ecosystem} and \textbf{Automated Quality Assurance}. Expert in delivering robust, high-availability software through \textbf{Test-Driven Development (TDD)}, comprehensive \textbf{Unit \& Integration Testing (xUnit, NUnit)}, and advanced system monitoring via \textbf{Grafana}. Proven expertise in the automotive industry (Ecarx/Geely) optimizing MTTR and system stability through proactive observability. Passionate about building reliable, maintainable codebases within collaborative, human-centric teams. Committed to the highest standards of software craftsmanship and mission-critical performance.

\section*{Quality \& Fullstack Skills}
\begin{itemize}[leftmargin=*, itemsep=2pt]
\item \textbf{Testing \& Quality:} \textbf{xUnit, NUnit}, FluentAssertions, Moq, Integration Testing, \textbf{TDD}, Automated UI Testing, API Testing (Postman/Newman)
\item \textbf{Monitoring \& Observability:} \textbf{Grafana}, Prometheus, ELK Stack, OpenTelemetry, Performance Profiling, System Health Dashboards
\item \textbf{Backend Development:} \textbf{C\# .NET 8}, ASP.NET Core, Entity Framework Core, \textbf{Kafka}, Microservices, RESTful APIs, Clean Architecture
\item \textbf{Cloud \& DevOps:} \textbf{Azure} (AKS, App Services, Functions), CI/CD with Quality Gates (GitHub Actions, Azure DevOps), Docker, Kubernetes
\item \textbf{Data Systems:} SQL Server (Schema Design, Optimization), PostgreSQL, Redis, MongoDB
\item \textbf{Frontend Engineering:} React, Vue.js, TypeScript, Redux Toolkit, Automated Frontend Testing (Jest, Testing Library)
\item \textbf{Languages:} Fluent English and Mandarin, Swedish B2 level
\end{itemize}

\section*{Professional Experience}

\subsection*{ECARX (Geely Automotive) | Infrastructure Specialist \& Quality Engineer}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Observability \& Quality Strategy:} Designed and implemented comprehensive monitoring frameworks using \textbf{Grafana} and Prometheus, reducing critical incident response time by 35\%.
\item \textbf{Reliability Engineering:} Provided 24/7 on-call production support for mission-critical automotive platforms, ensuring system stability through rigorous testing and observability.
\item \textbf{CI/CD Quality Gates:} Integrated automated testing suites into deployment pipelines, ensuring that only verified code reached production Kubernetes environments.
\item \textbf{Automotive Quality Standards:} Adhered to high-compliance software standards, delivering stable dashboard solutions for real-time data visualization.
\end{itemize}

\subsection*{Synteda AB | C\# .NET Developer \& Azure Specialist}
\textit{August 2023 - September 2024 | Gothenburg, Sweden (Remote)}
\begin{itemize}[noitemsep]
\item \textbf{Test-Driven Backend:} Developed talent management microservices using C\# .NET Core, prioritizing high test coverage and reliable data access via Entity Framework.
\item \textbf{Integration Excellence:} Built and tested RESTful APIs for complex talent ecosystems, ensuring seamless and bug-free communication across distributed services.
\item \textbf{Azure Stability:} Leveraged Azure DevOps for automated release management, incorporating automated testing as a core part of the deployment lifecycle.
\end{itemize}

\subsection*{Senior Material (Europe) AB | Fullstack Platform Architect}
\textit{January 2022 - December 2022 | Eskilstuna, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Modular Migration:} Led the transition to microservices for manufacturing platforms, implementing robust integration tests to ensure system integrity during the migration.
\item \textbf{Stability Focus:} Standardized testing patterns for React-based manufacturing dashboards and Spring Boot backends.
\end{itemize}

\section*{Strategic Projects}

\subsection*{Fleet Management System (Quality Focus)}
\textit{2024 - 2025} | \textbf{.NET 8, React, SQL Server, Azure, Docker, Sustainability Analytics}
\begin{itemize}[noitemsep]
\item \textbf{Reliable Analytics:} Built a data-intensive dashboard for CO2 tracking and fuel analysis, using US DOT datasets with rigorous data validation and testing protocols.
\item \textbf{Stability:} Implemented automated monitoring for fleet performance, demonstrating a commitment to system health and data accuracy.
\end{itemize}

\subsection*{AI Math Grader Ecosystem}
\textit{2025} | \textbf{AI/LLM Integration, TypeScript, Cloud Deployment}
\begin{itemize}[noitemsep]
\item Developed an automated grading tool with a focus on output consistency and fallback mechanisms for AI-driven feedback loops.
\end{itemize}

\section*{Education}
\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Focus: Automated Testing, .NET Core, Azure Infrastructure, Cloud Architectures}\\[5pt]
\textbf{University of Gothenburg} | Master's in International Business and Trade | 2016-2019

\section*{Why Join Your Team?}
\begin{itemize}[noitemsep]
\item \textbf{Quality-First Mindset:} I am passionate about building software that is not just functional, but demonstrably stable and maintainable.
\item \textbf{Technical Fit:} Expert in **.NET 8**, **xUnit/NUnit**, **Grafana**, and **Kafka**, aligning with your focus on quality and observability.
\item \textbf{Collaborative Values:} I thrive in human-centric teams where trust and curiosity drive innovation and high-quality results.
\item \textbf{Local Presence:} Based in Gothenburg and eager to join the vibrant tech community at Lindholmen.
\end{itemize}

\end{document}
