\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

% Page setup
\geometry{margin=0.75in}
\pagestyle{empty}

% Color definitions
\definecolor{linkedinblue}{RGB}{0,119,181}
\definecolor{lightgray}{RGB}{128,128,128}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkedinblue,
    urlcolor=linkedinblue,
    citecolor=linkedinblue
}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{linkedinblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

\begin{document}
\pagestyle{empty}

% Name and contact details
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[10pt]
{\Large \textit{Senior .NET Infrastructure \& Performance Engineering Specialist}}\\[10pt]
\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} --- \href{tel:0728384299}{0728384299} --- \href{https://www.linkedin.com/in/hzl/}{LinkedIn} --- \href{https://github.com/bluehawana}{GitHub}
\end{center}

% Personal Profile
\section*{Profile Summary}
Multi-disciplined \textbf{Fullstack Developer} with over 4 years of experience, specializing in the \textbf{.NET 8 ecosystem} and \textbf{Cloud Infrastructure}. Expert in bridging the gap between application development and production reliability through \textbf{Azure}, \textbf{Kubernetes}, and \textbf{Infrastructure as Code (Terraform)}. Proven track record in the automotive industry (Ecarx/Geely), managing globally distributed environments and optimizing CI/CD workflows. Passionate about building scalable, sustainable systems and thriving in collaborative, human-centric teams.

% Areas of Expertise
\section*{Core Technical Skills}
\begin{itemize}[noitemsep]
\item \textbf{Backend:} C\#/.NET Core, ASP.NET, RESTful APIs, Microservices, Event-Driven Architecture
\item \textbf{Frontend:} React, Vue.js, JavaScript, TypeScript, HTML5, CSS3, Responsive Design
\item \textbf{Infrastructure:} Kubernetes, Azure (AKS, App Services, Functions), Terraform (IaC), Docker
\item \textbf{Observability \& Monitoring:} Grafana, Prometheus, OpenTelemetry, ELK Stack, Performance Tuning
\item \textbf{CI/CD:} GitHub Actions, Azure DevOps, Jenkins, Automated Testing Pipelines
\item \textbf{Databases:} SQL Server, PostgreSQL, MongoDB, Redis, Entity Framework Core
\item \textbf{Cloud \& DevOps:} Azure (AKS, App Services, Functions, SQL), Infrastructure as Code (Terraform), Docker, Kubernetes
\item \textbf{Distributed Systems:} Scalability, Resilience, Load Balancing, Caching Strategies, Kafka
\item \textbf{Testing:} xUnit, NUnit, Jest, TDD, Integration Testing, Automated Test Suites
\item \textbf{Agile:} Scrum, Kanban, Sprint Planning, Cross-functional Collaboration
\item \textbf{Languages:} Fluent in English and Mandarin Chinese; Swedish (B2 level)
\end{itemize}

% Experience
\section*{Professional Experience}
\subsection*{ECARX (Geely Automotive) | Infrastructure Specialist \& Cloud Engineer}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Azure to On-Premise Migration:} Led migration of critical workloads from Azure AKS to on-premise HPC infrastructure, achieving 65\% cost reduction and 259\% performance improvement through systematic optimization and tuning.
\item \textbf{Cloud Architecture \& Cost Optimization:} Designed and implemented Azure cloud architecture for automotive development platforms, optimizing resource allocation and reducing operational expenses by 48\% compared to Azure HB120rs\_v3 instances.
\item \textbf{HPC Performance Tuning:} Optimized local HPC infrastructure for Android AOSP builds, achieving record-breaking 7.78-minute build times through infrastructure automation and performance tuning.
\item \textbf{DevOps Team Collaboration:} Worked closely with DevOps team to implement Infrastructure as Code (Terraform), automated CI/CD pipelines with GitHub Actions and GitLab Runner, and establish monitoring standards with Grafana and Prometheus.
\item \textbf{Kubernetes Infrastructure Leadership:} Managed globally distributed Kubernetes clusters for automotive platforms, ensuring 99.9\% availability across 4 international regions with comprehensive observability and incident response.
\item \textbf{Site Reliability Engineering:} Established SRE practices and monitoring standards, leading to 35\% reduction in MTTR for critical incidents through proactive monitoring and automated alerting.
\end{itemize}

\subsection*{Synteda AB | C\# .NET Fullstack Developer \& Azure Specialist}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Scalable Cloud Solutions:} Developed talent management microservices using C\# .NET Core, deployed on Azure App Services with full automated CI/CD.
\item \textbf{Database Architecture:} Designed and optimized Azure SQL databases, ensuring performant data access via Entity Framework.
\item \textbf{API Integration:} Built secure RESTful APIs for internal and external consumption, prioritizing scalability and infrastructure alignment.
\end{itemize}

\subsection*{IT-Högskolan | Backend Developer (Part-time)}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Migrated "Omstallningsstod.se" adult education platform using Spring Boot backend services with microservices architecture.
\item Developed RESTful APIs for frontend integration and implemented secure data handling with automated testing.
\item Collaborated with UI/UX designers to ensure seamless frontend-backend integration and optimal user experience.
\end{itemize}

\subsection*{Senior Material (Europe) AB | Fullstack Platform Architect}
\textit{January 2022 - December 2022 | Eskilstuna, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Infrastructure Migration:} Led the migration of monolith manufacturing platforms to a containerized microservices architecture in the battery industry.
\item \textbf{Fullstack Delivery:} Developed React frontends and Spring Boot backends, ensuring seamless integration across the entire stack.
\end{itemize}

\section*{Strategic Projects}

\subsection*{Fleet Management Dashboard}
\textit{2024 -- Present} \\
\textbf{.NET 8, React 18, SQL Server 2022, Azure, Docker, GitHub Actions}
\begin{itemize}[noitemsep]
\item Built intelligent fleet tracking platform using US DOT data to optimize fuel efficiency and CO2 tracking for sustainable transport operations.
\item Implemented microservices architecture with event-driven patterns for real-time data processing and predictive maintenance analytics.
\item Leveraged Azure App Service and Docker for scalable hosting, with fully automated CI/CD pipelines via GitHub Actions.
\item Integrated Grafana dashboards for operational monitoring and performance metrics visualization.
\end{itemize}

\subsection*{AI Math Grader Ecosystem}
\textit{2025 -- Present} \\
\textbf{C\# .NET 8, React, AI/LLM (Gemini/OpenAI), Python, PDF Export}
\begin{itemize}[noitemsep]
\item Developed full-stack automated grading system for K-12 math, providing instant pedagogical feedback using advanced LLM integration.
\item Architected modular API layer with C\# .NET for AI-driven feedback loops, ensuring low-latency processing and high accuracy.
\item Built React frontend with responsive design and integrated white-label PDF export functionality for accessible result sharing.
\end{itemize}

\section*{Hobby Projects}

\subsection*{SmrtMart E-commerce Platform}
\textit{April 2024 -- Present} \\
\textbf{Go, Next.js, PostgreSQL, Microservices, Stripe API, Kubernetes}
\begin{itemize}[noitemsep]
\item Fullstack e-commerce platform with microservices-based architecture for seamless scalability and distributed order processing.
\item Implemented comprehensive order management, inventory tracking, and payment systems with Stripe integration.
\item Optimized backend API performance and integrated PostgreSQL and MongoDB for hybrid data storage supporting high transaction volumes.
\item Deployed on Kubernetes with Terraform IaC, implementing load balancing and auto-scaling for resilient distributed systems.
\item Live demo: \href{https://www.smrtmart.com}{www.smrtmart.com}
\end{itemize}

\subsection*{JobHunter Automation Platform}
\textit{July 2025 -- Present} \\
\textbf{Python, TypeScript, React, Gmail REST API, LinkedIn API}
\begin{itemize}[noitemsep]
\item Automated job hunting pipeline integrating Gmail search, job scraping, and resume customization with NLP techniques.
\item Built React-based dashboard for application tracking and management with real-time updates.
\end{itemize}

\section*{Education}
\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Focus: C\# backend development, cloud architecture, microservices, Azure, databases}

\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textit{Focus: Enterprise integration, Spring Framework, RESTful APIs, SQL databases}

\textbf{University of Gothenburg} | Master's in International Business \& Trade | 2016-2019\\
\textit{Focus: Business analysis, international commerce, B2B operations}

\section*{Cloud Certifications}
\begin{itemize}[noitemsep]
\item AWS Certified Solutions Architect - Associate (Aug 2022)
\item AWS Certified Developer - Associate (Nov 2022)
\item Microsoft Certified: Azure Fundamentals (Jun 2022)
\end{itemize}

\end{document}
