\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{parskip}

% Page setup
\geometry{margin=1in}
\pagestyle{empty}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

\begin{document}

% Header
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[5pt]
\textcolor{darkblue}{Software Engineer | Automotive Enthusiast}\\[5pt]
\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | Gothenburg, Sweden
\end{center}

\vspace{20pt}

\today

\vspace{10pt}

\textbf{Saab AB}\\
Gothenburg, Sweden

\vspace{20pt}

\textbf{Re: Application for "Develop your passion for software into reality" - Software Engineer}

\vspace{10pt}

Dear Hiring Team,

When I saw the headline "Develop your passion for software into reality," it resonated deeply with my own professional philosophy. As a Software Engineer currently working at the intersection of high-performance computing and automotive technology at ECARX, I don't just write code; I build systems that bridge the gap between ambitious ideas and tangible, safety-critical realities. I am writing to express my strong enthusiasm for joining Saab and contributing to your mission of keeping people safe and society secure.

My current role involves optimizing the very foundation of automotive software development—the Android Open Source Project (AOSP) build system. By migrating build tasks to Azure AKS and optimizing hardware configurations, I achieved a 3.5x performance improvement, reducing clean build times to under 8 minutes. This experience has honed my ability to look at complex systems holistically, identify bottlenecks, and implement robust, scalable solutions. I understand that at Saab, software is not just about functionality; it's about reliability, precision, and performance in critical environments.

I am particularly drawn to Saab's commitment to innovation and the opportunity to "find your own path." My journey has taken me from mobile app development to architecting cloud infrastructure and now to the cutting edge of automotive software. I am currently teaching myself C++ to deepen my understanding of native system-level programming, reflecting my proactive approach to learning and my desire to tackle lower-level challenges in embedded systems.

Your focus on collaboration and "brilliant minds" aligns perfectly with my way of working. Whether it's coordinating with hardware engineers to validate physical emulators or designing hybrid cloud architectures with DevOps specialists, I thrive in cross-functional teams where diverse expertise converges to solve difficult problems.

I am eager to bring my technical skills in Android, System Performance, and Cloud Architecture, along with my passion for automotive and safety technologies, to Saab. I would welcome the opportunity to discuss how my background and enthusiasm can contribute to your team in Gothenburg.

Thank you for your time and consideration.

Sincerely,

Harvad (Hongzhi) Li

\end{document}
