\documentclass[a4paper,10pt]{letter}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.2, 0.6}
\setlength{\parindent}{0pt}
\begin{document}
\pagestyle{empty}
\begin{letter}{Kollmorgen\\Gothenburg, Sweden}
\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Junior Software Engineer -- Operation \& Visualization position at Kollmorgen. With hands\-on experience in visualization systems, real\-time monitoring dashboards, and automotive UI development, I am excited about the opportunity to contribute to your AGV operation software.

At ECARX, I have been deeply involved in creating visualization and monitoring solutions for complex automotive systems. I designed and implemented real\-time performance dashboards using Grafana and Prometheus for Android AOSP build infrastructure, providing intuitive visual feedback that enabled our team to achieve a 3.5x performance improvement. These dashboards process and visualize terabytes of build data daily, with our Android 15 AOSP clean build time reaching 7 minutes 47 seconds -- among the fastest publicly reported times.

Beyond infrastructure monitoring, I have extensive experience building user\-facing applications with modern frameworks. My hobby projects demonstrate this breadth: I developed Android Auto applications with automotive\-optimized UI/UX compliant with safety standards, created a cross\-platform carpooling mobile app with real\-time geolocation tracking and interactive maps using React Native, and built e\-commerce platforms with real\-time analytics dashboards. Each project required balancing technical complexity with user\-friendly design.

What excites me most about this role is applying my visualization skills to robotics and autonomous systems. Having worked with automotive testing platforms including Polestar 4/5 emulators, I understand the importance of reliable, intuitive interfaces for complex systems. I am eager to bring my real\-time data visualization experience, UI/UX skills, and passion for automation to help Kollmorgen deliver world\-class AGV operation software.

I am a collaborative team player who thrives in cross\-functional environments, fluent in English and Mandarin with Swedish B2 proficiency. I would be thrilled to contribute to your team in Gothenburg.

\closing{Sincerely,}
\signature{Hongzhi Li\\Ebbe Lieberathsgatan 27\\412 65 G\"{o}teborg\\hongzhili01@gmail.com\\0728384299\\2025.11.19}
\end{letter}
\end{document}
