\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (simple left-aligned, Omegapoint style)
Kollmorgen\\
Software Developer\\
Gothenburg, Sweden

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}
I was really excited to see the Junior Software Engineer - Operation & Visualization role at Kollmorgen. My background in building real-time monitoring systems for automotive testing and Android development has given me a deep appreciation for clear, actionable data visualization – something I imagine is absolutely critical in the world of AGVs and robotics. Thinking about the challenges of presenting complex robotic operations in an intuitive way for operators is genuinely interesting to me.

Beyond the technical aspects, I've learned how important it is to bridge the gap between IT and the business side. At ECARX, and even during my freelance work with Mibo.se where I helped integrate a full Microsoft solution, I've focused on making sure the tech solutions directly address business needs and are easily understood by everyone involved. That project, in particular, highlighted the value of collaborative problem-solving and clear communication across teams.

My experience spans from building performance-optimized dashboards using Grafana and Prometheus (leading to significant performance gains in build systems) to developing user-friendly automotive applications with a focus on UI/UX. I'm confident that my skills in real-time systems, coupled with my ability to connect with people and facilitate communication, would make me a valuable asset to your team. I'm eager to learn more about how I can contribute to Kollmorgen's innovative work.

\closing{
\vspace{1cm}

Best Regards,\\[0.5cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date
\noindent Ebbe Lieberathsgatan 27, 41265 Gothenburg, Sweden \hfill \today

\end{document}