\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (simple left-aligned, Omegapoint style)
Kollmorgen\\
Software Developer\\
Gothenburg, Sweden

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}
I am writing to express my strong interest in the Junior Software Engineer -- Operation \& Visualization position at Kollmorgen. With hands\-on experience in visualization systems, real\-time monitoring dashboards, and automotive UI development, I am excited about the opportunity to contribute to your AGV operation software.

At ECARX, I have been deeply involved in creating visualization and monitoring solutions for complex automotive systems. I designed and implemented real\-time performance dashboards using Grafana and Prometheus for Android AOSP build infrastructure, providing intuitive visual feedback that enabled our team to achieve a 3.5x performance improvement. These dashboards process and visualize terabytes of build data daily, with our Android 15 AOSP clean build time reaching 7 minutes 47 seconds -- among the fastest publicly reported times.

Beyond infrastructure monitoring, I have extensive experience building user\-facing applications with modern frameworks. My hobby projects demonstrate this breadth: I developed Android Auto applications with automotive\-optimized UI/UX compliant with safety standards, created a cross\-platform carpooling mobile app with real\-time geolocation tracking and interactive maps using React Native, and built e\-commerce platforms with real\-time analytics dashboards. Each project required balancing technical complexity with user\-friendly design.

What excites me most about this role is applying my visualization skills to robotics and autonomous systems. Having worked with automotive testing platforms including Polestar 4/5 emulators, I understand the importance of reliable, intuitive interfaces for complex systems. I am eager to bring my real\-time data visualization experience, UI/UX skills, and passion for automation to help Kollmorgen deliver world\-class AGV operation software.

I am a collaborative team player who thrives in cross\-functional environments, fluent in English and Mandarin with Swedish B2 proficiency. I would be thrilled to contribute to your team in Gothenburg.

\closing{
\vspace{1cm}

Best Regards,\\[0.5cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date
\noindent Ebbe Lieberathsgatan 27, 41265 Gothenburg, Sweden \hfill \today

\end{document}