\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
Ascom (Sweden) AB\\
ICT Operations Team\\
Grimbodalen 2\\
SE-417 05 Gothenburg, Sweden}

\vspace{30pt}

\opening{Dear Hiring Manager,}

\vspace{8pt}

I am excited to apply for the ICT Software Engineer position at Ascom. Your vision of closing digital information gaps to enable the best possible decisions resonates deeply with my passion for maintaining reliable, mission-critical applications that users can depend on.

What makes me particularly suited for this role is my hands-on experience managing application lifecycles while still actively coding where it adds value. At ECARX, I've achieved 99.97\% uptime for production systems through careful incident management, comprehensive documentation, and well-planned releases. My approach to application management perfectly aligns with your needs—I translate user requirements into stable, supportable solutions using C\#/.NET and SQL, always with complete rollback plans and thorough testing across DEV/TEST/PROD environments.

Your emphasis on "reliability by design" matches my philosophy exactly. I've built verification plans and test automation frameworks that ensure clean deployments, while my SQL optimization work has improved business-critical workflow performance by 3.5x. I understand that the real superpower isn't just writing code—it's turning requirements into solutions that stand up in production while continuously gathering user feedback for incremental improvements.

The collaborative nature of this role excites me. Currently, I coordinate with vendors and cross-functional stakeholders daily, communicating trade-offs and timelines clearly. My experience spans the full SDLC with agile methodologies, and I maintain strong documentation discipline—something I believe is crucial for enterprise application supportability. My fluency in English, combined with my technical foundation in .NET/C\# and SQL Server, enables me to translate complex technical issues into clear business language.

I'm eager to bring my application management expertise to Ascom, contributing to your global ICT operations while ensuring your mission-critical communication systems remain healthy, secure, and continuously improving. As someone who values innovation, accountability, and making a real impact, I'm excited about the opportunity to be that "steady hand" behind applications used globally.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}