\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
SKF AB\\
Automotive Business Division\\
Sven Wingqvists gata 2\\
SE-415 26 Gothenburg, Sweden}

\vspace{30pt}

\opening{Dear Hiring Manager,}

\vspace{8pt}

I am writing to express my strong interest in the Senior Full Stack Cloud Developer position at SKF's Automotive Business. As a complete full-stack practitioner at ECARX, I bring exactly what SKF needs: deep expertise across frontend (React/Angular/Vue.js), backend (Python/Java/C\#), DevOps (Docker/Kubernetes/CI/CD), and multi-cloud architectures (Azure/AWS/OCI).

What sets me apart is my ability to bridge every gap in technology organizations. I write production code across the entire stack, architect cloud solutions that balance performance with cost, and translate complex technical decisions into clear business value. When our Azure AKS migration achieved 3.5x performance improvement while reducing costs by 48\%, it wasn't just technical excellence—it was understanding how to align infrastructure decisions with business objectives.

Beyond technical skills, I've become the natural bridge between our Chinese and Swedish teams at ECARX. In meetings, I help Chinese engineers articulate their innovative solutions to Swedish stakeholders, and translate Swedish quality requirements into actionable plans for our Chinese development teams. This cultural translation goes beyond language—it's about understanding that when Chinese colleagues say "no problem," they might need support, and when Swedish colleagues request "further discussion," they have specific concerns. Combined with my DevOps expertise, I don't just implement CI/CD pipelines—I ensure both teams understand and embrace the automation benefits, reducing deployment time from days to minutes while building trust across cultures.

Your multi-cloud requirement perfectly matches my philosophy: being cloud-agnostic while cloud-expert. I've deployed production systems on Azure (AKS, Functions, SQL Database), AWS (Lambda, EC2), and understand OCI's price-performance advantages. More importantly, I architect solutions that leverage each platform's strengths while avoiding vendor lock-in—critical for SKF's global operations.

I'm excited to bring my complete technology expertise to SKF—not just coding frontend and backend, but understanding the entire ecosystem from UI to infrastructure, from DevOps to business strategy. I'm ready to be the bridge that connects your technical excellence with business transformation.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}