\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
Telia Company\\
Attn: Tomas Brimor\\
Engineering Manager - Team Enrichment \& API\\
Stjärntorget 1\\
SE-169 79 Solna, Sweden}

\vspace{30pt}

\opening{Dear Tomas and Team,}

\vspace{8pt}

I am excited to apply for the Backend Developer position with Team Enrichment \& API at Telia Play. Your vision of creating lightning-fast metadata systems that power seamless content experiences across the Nordics resonates perfectly with my passion for building high-performance backend systems that directly impact user experience.

What makes me particularly suited for this role is my hands-on experience with your exact tech stack. At ECARX, I've built microservices using Java/Spring Boot with AWS services including SNS, SQS, and event-driven architectures—precisely the technologies you use for metadata processing. My recent project achieved 3.5x performance improvements in high-throughput data processing pipelines, demonstrating my ability to optimize systems for the speed and reliability that metadata delivery demands.

Your focus on data quality and real-time processing aligns with my experience in building systems where accuracy and performance are critical. I understand that when metadata is missing or delayed, it's instantly visible to users—which is why I've always prioritized building robust, fault-tolerant systems with comprehensive monitoring. My work with PostgreSQL optimization and implementing Infrastructure as Code with Terraform ensures that backend systems can handle the aggregation, normalization, and enrichment processes your team manages.

The collaborative aspect of your team excites me greatly. I thrive in environments that value technical excellence and curiosity, and I've consistently demonstrated my ability to think beyond individual features to improve systems holistically. My experience with GitHub Copilot and AI-assisted development tools means I can leverage these technologies to accelerate development while maintaining the high code quality standards your team values.

Your mission to shape how content is organized, connected, and delivered speaks to my desire for meaningful impact. Having worked with international teams and understanding the importance of scalable, reliable systems, I'm eager to contribute to the metadata ecosystem that enables millions of users across the Nordics to discover and enjoy content seamlessly.

I'm excited about the opportunity to join Team Enrichment \& API and help build the foundational systems that power Telia TV's content discovery and delivery experience.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}