\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
Thomson Reuters - Pagero AB\\
Platform Engineering Team\\
Västra Hamngatan 1\\
SE-411 17 Gothenburg, Sweden}

\vspace{30pt}

\opening{Dear Hiring Manager,}

\vspace{8pt}

I am excited to apply for the Platform Engineer position at Thomson Reuters - Pagero. Your vision of providing a self-service platform where product teams can develop, manage, and monitor their services aligns perfectly with my passion for accelerating engineering productivity through innovative tooling and infrastructure automation.

What makes me particularly suited for this role is my hands-on experience building platforms that enable developers to ship code quickly and reliably. At ECARX, I've led a comprehensive platform transformation including Azure AKS to hybrid cloud migration, achieving 3.5x performance improvements while building self-service toolchains that reduce cognitive overhead for our 15+ development teams. I've implemented the exact type of observability stack you're looking for—Prometheus/Grafana for metrics, centralized logging, distributed tracing, and intelligent alerting that gives developers relevant information about their systems.

Your focus on hybrid cloud environments and multi-regional support resonates with my current work. I've architected platforms that support global operations, implementing Infrastructure as Code practices that enable teams to adapt their services for multi-regional data locality and processing. My approach to platform engineering centers on abstracting developer intent from implementation details—creating that crucial path from zero to production that your team envisions.

The collaborative culture at Pagero excites me greatly. I thrive in environments where code reviews, pair programming, and design discussions are natural ways to share knowledge. Currently, I work across diverse technical ecosystems and enjoy exploring new technologies while documenting and promoting best practices. My experience spans multiple software ecosystems, from automotive embedded systems to cloud-native microservices, giving me the adaptability to tackle complex problems requiring tight collaboration with product teams.

I'm eager to bring my platform engineering expertise to Thomson Reuters - Pagero, contributing to your mission of building the world's largest open business network while enabling your 100+ engineers to focus on what they build best—innovative solutions that help customers navigate global business complexity.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}