\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
Volvo Financial Services\\
Integration Office Chapter Lead\\
Gropegårdsgatan 2\\
SE-417 10 Gothenburg, Sweden}

\vspace{30pt}

\opening{Dear Hiring Manager,}

\vspace{8pt}

I am excited to apply for the Global Integration Architect position at Volvo Financial Services. With my rare dual industry expertise—combining current automotive technology experience at ECARX with previous banking industry background—I bring exactly the comprehensive perspective VFS needs. My background as a Corporate Finance Specialist and Marketing Manager in Chinese banking, coupled with my current role architecting integration platforms in the automotive sector, positions me uniquely to understand both industries that define Volvo Financial Services: automotive innovation and financial operations.

What makes me particularly suited for this role is my deep understanding of financial services combined with hands-on Azure integration expertise. Having worked in banking operations—managing loan processing, credit analysis, and financial workflows—I understand the criticality of secure, compliant, and scalable integration in financial services. At ECARX, I've implemented serverless solutions using Azure Functions integrated with Apache Kafka, building real-time event processing systems. While I haven't worked with IBM MQ or API Connect specifically, my expertise with Kafka and Azure Functions, combined with my financial domain knowledge, ensures I can quickly master your integration stack while bringing valuable banking insights.

My architectural approach aligns perfectly with VFS's needs. I've designed microservices architectures, implemented API gateway patterns using Azure API Management, and built event-driven systems that scale globally. Recently, I led our Azure AKS migration project where strategic integration design resulted in 3.5x performance improvement while maintaining 99.97\% uptime. This experience taught me how to balance technical excellence with business value—exactly what the CAST model requires.

The cross-functional nature of this role excites me. Currently, I work daily with hardware engineers, DevOps specialists, and business stakeholders, translating complex integration requirements into practical solutions. My fluency in English, Mandarin, and Swedish has been invaluable when coordinating with global teams, ensuring architectural decisions consider diverse perspectives and regional requirements.

I'm eager to bring my unique dual-industry perspective to VFS—someone who understands both the automotive innovation that drives your customers and the financial operations that serve them. My banking background means I speak the language of your financial stakeholders, while my automotive technology experience ensures I understand your customers' evolving needs. This rare combination of automotive and financial domain knowledge, coupled with my technical integration expertise, means I'll quickly master your IBM integration stack while contributing valuable cross-industry insights that can drive innovation in financial services for the automotive sector.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}