\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

\begin{letter}{\color{darkblue}
Volvo Energy AB\\
Attn: Axel Kullander\\
Head of Digital Products – Battery Technology\\
SE-405 08 Gothenburg, Sweden}

\vspace{30pt}

\opening{Dear Axel and Hiring Team,}

\vspace{8pt}

I am excited to apply for the Digital Support Lead position at Volvo Energy. Your mission to accelerate electrification and drive sustainability aligns perfectly with my passion for technology that makes a difference. With my current role at ECARX in the automotive sector and previous experience at Senior Material in Eskilstuna, I bring relevant skills in Azure infrastructure, technical support, and cross-functional collaboration.

At ECARX, I'm leading a significant Azure AKS migration project where documentation and knowledge sharing have been crucial for success. I've created comprehensive training materials, conducted technical sessions for our engineering teams, and established monitoring systems with Prometheus/Grafana. This experience has taught me the importance of clear communication and proactive support—essential qualities for managing incident response and maintaining operational excellence.

My time at Senior Material Europe AB in Eskilstuna was particularly valuable as it exposed me to international business operations and the challenges of coordinating between Chinese suppliers and Swedish teams. I served as a bridge, helping translate technical requirements and ensuring smooth collaboration across cultural and language barriers. This experience, combined with my fluency in English, Mandarin, and Swedish (B2), positions me well to support Volvo Energy's global operations.

What excites me most about this role is the opportunity to combine my technical skills with my passion for sustainable transport. I understand that supporting complex systems like Battery Energy Storage requires not just technical expertise, but also the ability to create clear documentation, train teams effectively, and maintain a customer-focused mindset during critical incidents. My "boots on the ground" approach means I'm ready to dive deep into problems while keeping the bigger picture in mind.

I'm eager to bring my Azure expertise, documentation skills, and collaborative approach to Volvo Energy, contributing to your mission of creating a fossil-free future while ensuring operational excellence in your digital platforms.

\vspace{10pt}

\closing{
Sincerely,\\
\vspace{15pt}
Harvad (Hongzhi) Li
}

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}
\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728384299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}
}

\end{letter}

\end{document}