\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{parskip}

% Page setup
\geometry{margin=1in}
\pagestyle{empty}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue
}

\begin{document}

% Header
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[5pt]
\textcolor{darkblue}{Full Stack Engineer | Sustainability Advocate}\\[5pt]
\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | Gothenburg, Sweden
\end{center}

\vspace{20pt}

\today

\vspace{10pt}

\textbf{Cetasol AB}\\
Åvägen 17C\\
Gothenburg, Sweden

\vspace{20pt}

\textbf{Re: Application for Full Stack Engineer}

\vspace{10pt}

Dear Hiring Team,

I have been following Cetasol's journey in revolutionizing the maritime industry through AI and sustainability, and I am thrilled to apply for the Full Stack Engineer position. As a developer who is deeply passionate about using technology to solve real-world problems—specifically in efficiency and sustainability—I see Cetasol as the perfect environment to apply my skills in full-stack development and cloud architecture.

In my current role at ECARX, and through my freelance projects, I have honed a versatile skill set that aligns directly with your stack. I have extensive experience building scalable applications using **TypeScript, React, and Node.js**, as well as developing robust backends with **Python**.

For instance, I recently developed "SmrtMart," a full-stack e-commerce platform using modern web technologies, where I focused on creating a seamless, responsive user experience backed by a microservices architecture. Additionally, my "Gothenburg TaxiPooling" project was born out of a desire to improve transport efficiency, utilizing real-time data to optimize routes—a concept that shares DNA with Cetasol's mission to optimize marine operations.

I am not just a coder; I am a problem solver who understands the importance of data. My experience with cloud infrastructure (Azure/AWS) and data visualization allows me to build systems that not only collect data but present it in actionable ways for users. I understand that for Cetasol, the user interface is the bridge between complex AI insights and the vessel operators who need to make sustainable decisions.

I am excited about the prospect of joining a dynamic startup like Cetasol, where my contributions can have a direct impact on the ocean's environment and the industry's future. I am eager to bring my energy, technical expertise, and passion for sustainability to your team in Gårda.

Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to Cetasol's continued success.

Sincerely,

Harvad (Hongzhi) Li

\end{document}
