\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome}

% Page setup
\geometry{margin=0.75in}
\pagestyle{empty}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{lightgray}{RGB}{128,128,128}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue
}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

% Custom commands
\newcommand{\contactitem}[2]{\textcolor{darkblue}{#1} #2}

\begin{document}
\pagestyle{empty} % no page number

% Name and contact details
\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[10pt]
{\Large \textit{Full Stack Engineer | Cloud & Sustainability Enthusiast}}\\[10pt]
\textcolor{darkblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728384299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}

% Personal Profile
\section*{Profile Summary}
Experienced Full Stack Engineer with a strong background in building scalable web and mobile applications. Passionate about using technology to drive sustainability and efficiency, making me highly aligned with Cetasol's mission. Proficient in modern full-stack technologies including TypeScript (React, Node.js), Python (FastAPI), and Cloud Architecture (Azure/AWS). Proven track record of delivering complex projects, from e-commerce platforms to automotive data systems. Adept at working in agile startup environments and translating business requirements into robust technical solutions.

% Areas of Expertise
\section*{Core Technical Skills}
\begin{itemize}[noitemsep]
\item \textbf{Frontend Development:} React, TypeScript, JavaScript, Next.js, Vue.js, HTML5, CSS3
\item \textbf{Backend Development:} Node.js, Python (FastAPI), Spring Boot, RESTful APIs, GraphQL
\item \textbf{Cloud & Infrastructure:} Azure, AWS, Docker, Kubernetes, Microservices, CI/CD
\item \textbf{Databases:} PostgreSQL, MongoDB, MySQL, Redis
\item \textbf{Sustainability Tech:} Energy efficiency optimization, Data-driven decision making
\item \textbf{Languages:} Fluent English and Mandarin Chinese, Swedish (B2 level)
\end{itemize}

% Experience
\section*{Working Experience}
\subsection*{ECARX | Senior Infrastructure & Performance Engineering Specialist}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Architected hybrid cloud solutions combining private cloud infrastructure with public cloud scalability.
\item Optimized system performance, reducing energy consumption and processing time for critical build tasks by 3.5x.
\item Developed Python-based automation tools for data analysis and system monitoring.
\end{itemize}

\subsection*{Synteda | Mobile App Developer \& Azure Integration Specialist (Freelance)}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Built comprehensive full-stack applications with React Native frontends and scalable cloud backends.
\item Implemented RESTful APIs and microservices architecture for client projects.
\item Integrated complex data visualization features for real-time monitoring.
\end{itemize}

\subsection*{IT-Högskolan | Mobile DevOps Support (Part-time)}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Supported full-stack development teams with CI/CD pipeline implementation and cloud deployment.
\item Facilitated API integration between frontend and backend services.
\end{itemize}

\section*{Relevant Projects}

\subsection{SmrtMart.com\_ECOMMERCE.WEB}
\textit{April 2024 -- Present} \\
\textbf{Go, Next.js, PostgreSQL, Microservices}
\begin{itemize}[noitemsep]
  \item Developed a full-stack e-commerce platform using Next.js for the frontend and Go microservices for the backend.
  \item Implemented a responsive, high-performance UI with seamless payment integration (Stripe).
  \item Optimized database queries and API response times for a superior user experience.
\end{itemize}

\subsection{Gothenburg\_TaxiPooling\_MobileApp}
\textit{May 2025 -- Present} \\
\textbf{React Native, Spring Boot, PostgreSQL, Geolocation APIs}
\begin{itemize}[noitemsep]
  \item Created a carpooling application focused on optimizing transport efficiency and reducing carbon footprint.
  \item Implemented real-time matching algorithms and geolocation tracking.
  \item Built a robust backend system to handle concurrent user requests and data processing.
\end{itemize}

\subsection{Weather\_Anywhere.CLOUD\_API\_Encoding}
\textit{Feb 2024 -- Present} \\
\textbf{Spring Boot, MySQL, Cloud Deployment}
\begin{itemize}[noitemsep]
  \item Built a weather tracking application aggregating data from multiple APIs.
  \item Deployed on cloud infrastructure with dynamic caching to minimize API calls and improve energy efficiency.
  \item Demo: \href{https://weather.bluehawana.com}{weather.bluehawana.com}
\end{itemize}

\vspace{6pt}
\section*{Education}
\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textbf{University of Gothenburg} | Master's in International Business and Trade | 2016-2019

\vspace{6pt}
\section*{Certifications}
\begin{itemize}
\item AWS Certified Solutions Architect - Associate (Aug 2022)
\item Microsoft Certified: Azure Fundamentals (Jun 2022)
\item AWS Certified Developer - Associate (Nov 2022)
\end{itemize}

\end{document}
