\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=0.6in}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\itemsep}{0pt}
\pagestyle{empty}

\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}
\titleformat{\section}{\Large\bfseries\color{linkedinblue}}{}{0em}{}[\vspace{-4pt}\titlerule\vspace{2pt}]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}[\vspace{-2pt}]

\begin{document}
\pagestyle{empty}

\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[8pt]
{\Large \textit{Fullstack Developer (Go, Java/Spring Boot, TypeScript)}}\\[8pt]
\textcolor{linkedinblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728 384 299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}
\vspace{8pt}

\section*{Profile Summary}
Fullstack Developer with 5+ years building scalable distributed systems using Go, Java/Spring Boot, and TypeScript. Deep expertise in Kubernetes orchestration, Docker containerization, and comprehensive observability with Grafana, Prometheus, and OpenTelemetry. Proven track record implementing CI/CD pipelines, monitoring solutions, and microservices architectures. Currently at ECARX managing globally distributed infrastructure with focus on performance optimization and system reliability.

\section*{Core Technical Skills}
\begin{itemize}[noitemsep]
\item \textbf{Backend:} Go, Java, Spring Boot, C\#/.NET Core, RESTful APIs, Microservices, Event-Driven Architecture
\item \textbf{Frontend:} TypeScript, React, Vue.js, JavaScript, Next.js, HTML5, CSS3, Responsive Design
\item \textbf{Container Orchestration:} Kubernetes (AKS, EKS, on-prem), Docker, Helm Charts, Container Security
\item \textbf{Monitoring \& Observability:} Grafana, Prometheus, Loki, OpenTelemetry, ELK Stack, Alerting, Dashboards
\item \textbf{CI/CD:} GitHub Actions, Azure DevOps, Jenkins, ArgoCD, Automated Testing Pipelines
\item \textbf{Infrastructure:} Azure, AWS, Terraform (IaC), Cloud Architecture, Load Balancing
\item \textbf{Databases:} PostgreSQL, SQL Server, MongoDB, Redis, Entity Framework, GORM
\item \textbf{Testing:} JUnit, Go testing, Jest, xUnit, TDD, Integration Testing, E2E Testing
\item \textbf{Agile:} Scrum, Kanban, Sprint Planning, Cross-functional Collaboration
\item \textbf{Languages:} Fluent in English and Mandarin Chinese; Swedish (B2 level)
\end{itemize}

\section*{Professional Experience}

\subsection*{ECARX (Geely Automotive) | IT/Infrastructure Specialist}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Managing globally distributed Kubernetes clusters across 4 international offices, implementing container orchestration best practices and resource optimization.
\item Implemented comprehensive observability stack using \textbf{Grafana, Prometheus, and Loki}, creating dashboards for real-time monitoring and achieving 25\% reduction in incident response time.
\item Architected CI/CD pipelines with GitHub Actions and Azure DevOps, enabling automated testing, container builds, and zero-downtime deployments for microservices.
\item Led Kubernetes migration from Azure AKS to on-premise clusters, achieving \textbf{65\% cost reduction} and \textbf{259\% performance improvement} through systematic optimization.
\item Providing 24/7 production support with proactive monitoring and alerting, ensuring high availability for mission-critical automotive services.
\item Implemented Docker containerization standards and Helm charts for consistent deployments across development, staging, and production environments.
\end{itemize}

\subsection*{Synteda | Fullstack Developer \& Integration Specialist}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Developed talent management platform using microservices architecture with RESTful APIs and event-driven patterns.
\item Built frontend components using TypeScript and React, implementing responsive design and modern UI patterns.
\item Established automated CI/CD pipelines via Azure DevOps with Docker containerization, ensuring reliable high-frequency releases.
\item Integrated monitoring and logging solutions for application observability and performance tracking.
\item Collaborated with stakeholders to translate business requirements into technical solutions, delivering B2B platform features.
\end{itemize}

\subsection*{IT-Högskolan | Backend Developer (Part-time)}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Migrated "Omstallningsstod.se" adult education platform using \textbf{Spring Boot} backend services with microservices architecture.
\item Developed RESTful APIs with \textbf{Java/Spring Boot} for frontend integration and implemented secure data handling with automated testing.
\item Collaborated with UI/UX designers to ensure seamless frontend-backend integration and optimal user experience.
\end{itemize}

\subsection*{Senior Material (Europe) AB | Fullstack Platform Architect}
\textit{January 2022 - December 2022 | Eskilstuna, Sweden}
\begin{itemize}[noitemsep]
\item Led digital transformation migrating monolithic applications to containerized microservices with \textbf{Docker} and Kubernetes.
\item Architected scalable backend solutions with \textbf{Spring Boot} and integrated modern React frontends with TypeScript.
\item Implemented monitoring and logging infrastructure for performance optimization and system observability.
\end{itemize}

\section*{Fullstack Projects with Go, TypeScript \& Observability}

\subsection*{SmrtMart E-commerce Platform}
\textit{April 2024 -- Present} \\
\textbf{Go, Next.js/TypeScript, PostgreSQL, Kubernetes, Docker, Stripe API, Prometheus}
\begin{itemize}[noitemsep]
\item Built fullstack e-commerce platform with \textbf{Go backend} and \textbf{TypeScript/Next.js frontend}, implementing microservices architecture.
\item Implemented comprehensive order management, inventory tracking, and payment systems with Stripe integration.
\item Deployed on \textbf{Kubernetes} with \textbf{Docker} containerization, implementing load balancing and auto-scaling for resilient distributed systems.
\item Integrated \textbf{Prometheus metrics} and health checks for monitoring and observability.
\item Live demo: \href{https://www.smrtmart.com}{www.smrtmart.com}
\end{itemize}

\subsection*{Fleet Management Dashboard}
\textit{2024 -- Present} \\
\textbf{.NET 8, React/TypeScript, SQL Server, Docker, GitHub Actions, Grafana}
\begin{itemize}[noitemsep]
\item Built intelligent fleet tracking platform with TypeScript frontend and .NET backend, deployed via Docker containers.
\item Implemented microservices architecture with event-driven patterns for real-time data processing.
\item Integrated \textbf{Grafana dashboards} for operational monitoring and performance metrics visualization.
\item Automated CI/CD pipelines with comprehensive testing and container builds via GitHub Actions.
\end{itemize}

\subsection*{Weather\_Anywhere.CLOUD}
\textit{2024 -- Present} \\
\textbf{Spring Boot (Java), React/TypeScript, MySQL, Docker, RESTful APIs}
\begin{itemize}[noitemsep]
\item Developed weather visualization platform with \textbf{Java/Spring Boot} backend and TypeScript/React frontend.
\item Containerized application with \textbf{Docker} for consistent deployment across environments.
\item Implemented caching strategies and RESTful APIs for optimal performance.
\item Demo: \href{https://weather.bluehawana.com}{weather.bluehawana.com}
\end{itemize}

\subsection*{JobHunter Automation Platform}
\textit{July 2025 -- Present} \\
\textbf{Python, TypeScript, React, Gmail REST API, Docker}
\begin{itemize}[noitemsep]
\item Automated job hunting pipeline with TypeScript/React frontend and Python backend, containerized with Docker.
\item Built real-time dashboard for application tracking with modern TypeScript patterns.
\item Demo: https://jobs.bluehawana.com
\end{itemize}

\section*{Additional Technical Projects}

\subsection*{AI Math Grader Ecosystem}
\textit{2025 -- Present} \\
\textbf{C\# .NET 8, React/TypeScript, AI/LLM Integration, Docker}
\begin{itemize}[noitemsep]
\item Developed fullstack automated grading system with TypeScript frontend and .NET backend.
\item Containerized with Docker for scalable deployment and consistent environments.
\end{itemize}

\subsection*{Invoice\_Handling\_System}
\textit{2025} \\
\textbf{C\# .NET, React/TypeScript, Docker, AI/OCR Integration}
\begin{itemize}[noitemsep]
\item Developed automated invoice processing system with TypeScript frontend, reducing manual data entry by 80\%.
\item Implemented Docker containerization for reliable deployment and scaling.
\end{itemize}

\section*{Education}

\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Focus: Backend development, cloud architecture, microservices, Docker, Kubernetes}

\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textit{Focus: Java, Spring Boot, enterprise integration, RESTful APIs, databases}

\textbf{University of Gothenburg} | Master's in International Business \& Trade | 2016-2019\\
\textit{Focus: Business analysis, international commerce, B2B operations}

\section*{Cloud Certifications}
AWS Certified Solutions Architect - Associate (Aug 2022) \\
AWS Certified Developer - Associate (Nov 2022) \\
Microsoft Certified: Azure Fundamentals (Jun 2022)

\end{document}
