\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (simple left-aligned, Omegapoint style)
DoiT International\\
International\\
Gothenburg, Sweden

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}
I'm writing to express my deep enthusiasm for the Full Stack Engineer (Frontend-Oriented) role at DoiT International. For the past 5+ years, I've been immersed in full-stack development, with a particular focus on building robust and intuitive React/TypeScript frontends. At ECARX, I'm currently contributing to real-time monitoring dashboards and cloud infrastructure, which has given me firsthand experience with the challenges and rewards of optimizing cloud environments on AWS, Azure, and GCP. The opportunity to apply that experience to cloud intelligence, especially with the integration of Cloudwize into DoiT, is incredibly exciting to me.

What truly resonates with me about DoiT is your commitment to cloud optimization and security. I've seen firsthand how critical these aspects are to successful cloud deployments, and I'm eager to leverage my experience designing RESTful/GraphQL APIs and crafting React-based interfaces to contribute to your mission. My personal projects, like SmrtMart (Go/Next.js) and the weather platform (Spring Boot/React), showcase my ability to build scalable and user-friendly applications. Even Mibo.se (C#/React/Azure), speaks to my adaptability and willingness to learn new technologies within the cloud ecosystem.

Beyond technical skills, I thrive in remote environments and collaborate effectively with international teams. Having worked extensively with both Swedish and Chinese teams, I understand the nuances of communication and project management across cultures. I'm a firm believer in being a "doer" – someone who takes initiative, seeks out new knowledge, and approaches challenges with a positive, entrepreneurial spirit. I’m confident that my skills and passion align perfectly with DoiT's culture and goals.

\closing{
\vspace{1cm}

Best Regards,\\[0.5cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date
\noindent Ebbe Lieberathsgatan 27, 41265 Gothenburg, Sweden \hfill \today

\end{document}