\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

{\color{linkedinblue}
\noindent [Company Name] \\
Hiring Manager \\
[Contact Email] \\
[Address] \\
[City], Sweden
}

\vspace{2cm}

Hej,

\vspace{0.5cm}

I am excited to apply for the [Position] position at [Company Name]. As a fullstack developer with a unique background bridging business and technology, I bring not just technical skills in React and backend development, but the ability to understand user needs and translate them into intuitive, data-driven applications.

My experience spans the full stack and international collaboration. At ECARX, I develop web-based monitoring interfaces for automotive platforms while managing hybrid cloud infrastructure. Working with teams across 4 global offices (Gothenburg, London, Stuttgart, San Diego), I've learned that the best frontend experiences come from understanding both technical constraints and business objectives. At Synteda, I built Mibo.se's talent management platform with C\# .NET backend and React frontend, ensuring alignment between business workflows and technical implementation.

What sets me apart is my ability to bridge technical and business worlds. My Master's in International Business, combined with fullstack development experience, means I don't just build features—I understand how UI/UX decisions affect user adoption, how performance impacts conversion rates, and how architecture choices affect maintainability costs. This cross-cultural communication ability and business-IT integration mindset enable me to spot real-world problems and architect practical solutions.

Beyond my professional work, I build practical systems driven by real needs. I created the AI Math Grader—a K-12 grading platform that addresses teachers' actual pain points with instant, pedagogical feedback. I also developed an Invoice Handling System using AI to streamline financial workflows, and SmrtMart.com—a live e-commerce platform with Stripe integration and microservices architecture. These projects demonstrate my ability to identify business demands and solve them with smooth, user-centric technical solutions.

I'm fluent in English and Mandarin Chinese, with Swedish B2 proficiency, enabling seamless collaboration in multicultural environments. I would love to discuss how my fullstack expertise, cross-cultural communication skills, and business-IT integration mindset can contribute to [Company Name]'s continued success.

\vspace{0.5cm}

Sincerely, \\
Harvad (Hongzhi) Li

\vspace{2cm}

{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

\noindent Gårdsvägen 9 \\
431 38 Mölndal, Sweden \\
hongzhili01@gmail.com \\
+46 72 838 4299

\end{document}
