\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

% Header with job information (simple left-aligned, LinkedIn blue)
{\color{linkedinblue}COMPANY_NAME\\
JOB_TITLE\\
Gothenburg, Sweden}

\vspace{1cm}

Dear Hiring Manager,

\vspace{0.5cm}

I am excited to apply for the JOB_TITLE position at COMPANY_NAME. What draws me to this role is the opportunity to \textbf{bridge the gap between IT and business}—exactly where my unique background positions me to excel.

Unlike typical IT professionals or pure business analysts, I bring both perspectives. My \textbf{Master's in International Business \& Trade} from University of Gothenburg taught me to think strategically about business value, stakeholder needs, and commercial impact. My two IT degrees and hands-on development experience mean I truly understand technical feasibility, system architecture, and what developers need to deliver solutions.

At ECARX, I serve as the bridge between technical infrastructure teams and business stakeholders across 4 global offices. I lead requirements workshops, conduct gap analyses between current capabilities and desired future states, and translate business needs into technical specifications. When I proposed a cloud migration, I didn't just present technical benefits—I created a business case showing 65\% cost reduction and ROI timeline that leadership could act on.

What sets me apart:
\begin{itemize}
\item \textbf{I speak both languages:} I can discuss microservices architecture with developers in the morning and present cost-benefit analysis to executives in the afternoon.
\item \textbf{I've built systems myself:} My hands-on IT experience (cloud platforms, databases, APIs) means I understand technical constraints and can evaluate solution feasibility realistically.
\item \textbf{I deliver business outcomes:} My projects demonstrate end-to-end thinking—from business requirements to technical implementation to measurable results.
\item \textbf{I communicate globally:} Fluent in English, Mandarin Chinese, and Swedish—essential for multinational stakeholder collaboration.
\end{itemize}

I'm passionate about leveraging digitalization for business success. I would welcome the opportunity to discuss how my IT-Business bridge capability can contribute to your strategic goals.

\vspace{1cm}

Best Regards,\\[0.5cm]
Harvad (Hongzhi) Li

\vspace{\fill}

% Line separator
{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

% Footer with address and date
{\color{linkedinblue}Ebbe Lieberathsgatan 27\\
41265, Gothenburg, Sweden\\
\hfill \today}

\end{document}