\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=0.6in}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}
\titleformat{\section}{\Large\bfseries\color{linkedinblue}}{}{0em}{}[\vspace{-4pt}\titlerule\vspace{2pt}]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}[\vspace{-2pt}]

\begin{document}
\pagestyle{empty}

\begin{center}
{\LARGE \textbf{Harvad (Hongzhi) Li}}\\[8pt]
{\Large \textit{IT Business Analyst | Bridging Technology \& Business}}\\[8pt]
\textcolor{linkedinblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728 384 299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}
\vspace{8pt}

\section*{Profile Summary}
IT Business Analyst with a unique combination of \textbf{Master's in International Business \& Trade} and hands-on IT development experience. Expert at \textbf{bridging the gap between technical IT systems and business requirements}. 5+ years translating complex business needs into technical specifications, leading requirements workshops, and driving digital transformation initiatives. Strong analytical skills with proven ability to understand both the technical implementation and the business/commercial impact. Experienced working with cross-functional teams across 4 global offices, stakeholder management, and process improvement.

\section*{Core Competencies}
\begin{itemize}[noitemsep]
\item \textbf{Business Analysis:} Requirements gathering, gap analysis, business case development, process mapping, stakeholder workshops
\item \textbf{IT-Business Bridge:} Translating business needs to technical specs, IT system evaluation, solution recommendations
\item \textbf{Tools \& Visualization:} Excel (Advanced), Power BI, Visio, JIRA, Confluence, Microsoft 365, Miro
\item \textbf{Technical Knowledge:} Cloud platforms (Azure, AWS), databases (SQL), APIs, microservices, CI/CD pipelines
\item \textbf{Project Management:} Agile/Scrum, pre-studies, change management, implementation support, UAT coordination
\item \textbf{Communication:} Workshop facilitation, stakeholder presentations, documentation, cross-cultural collaboration
\item \textbf{Languages:} Fluent English \& Mandarin Chinese; Swedish (B2) - enabling global stakeholder communication
\end{itemize}

\section*{Professional Experience}

\subsection*{ECARX (Geely Automotive) | IT/Infrastructure Specialist \& Business Liaison}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item \textbf{Bridging IT and Business:} Serving as liaison between technical infrastructure teams and business stakeholders across 4 global offices (Gothenburg, London, Stuttgart, San Diego).
\item Led requirements gathering sessions to understand business needs for infrastructure improvements, documenting objectives and success criteria.
\item Conducted gap analysis between current IT capabilities and desired future state, proposing cost-effective solutions.
\item Created technical documentation, process flows, and system diagrams using Visio for stakeholder communication.
\item Evaluated solution options for cloud migrations, presenting cost-benefit analysis to leadership (achieved 65\% cost reduction).
\item Collaborated with cross-functional teams to define technical specifications aligned with business objectives.
\item Implemented monitoring dashboards (Grafana) translating technical metrics into business-relevant KPIs.
\end{itemize}

\subsection*{Synteda | Business Analyst \& Integration Specialist}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Led requirements workshops with business stakeholders to define talent management platform specifications.
\item Translated business workflows into technical requirements for development team implementation.
\item Created detailed business requirements documentation, user stories, and acceptance criteria.
\item Performed gap analysis between existing processes and proposed IT solutions, identifying improvement areas.
\item Coordinated UAT (User Acceptance Testing) with business users, ensuring solutions met business needs.
\item Facilitated communication between technical developers and non-technical business stakeholders.
\end{itemize}

\subsection*{Senior Material (Europe) AB | Business Process \& IT Transformation Lead}
\textit{January 2022 - December 2022 | Eskilstuna, Sweden}
\begin{itemize}[noitemsep]
\item Led digital transformation initiative analyzing current business processes and identifying digitalization opportunities.
\item Conducted stakeholder interviews and workshops to understand manufacturing business requirements.
\item Documented current state vs. desired future state, creating business cases for IT investments.
\item Evaluated multiple solution options for system modernization, presenting recommendations to leadership.
\item Supported implementation of new IT systems, coordinating between technical teams and business users.
\end{itemize}

\subsection*{IT-Högskolan | Backend Developer \& Requirements Analyst}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Gathered and validated requirements for "Omstallningsstod.se" education platform enhancements.
\item Collaborated with UI/UX designers and business stakeholders to ensure solutions met user needs.
\item Created technical specifications based on business requirements documentation.
\end{itemize}

\section*{IT-Business Integration Projects}

\subsection*{Fleet Management Business Solution}
\textbf{Business Analysis + Technical Implementation}
\begin{itemize}[noitemsep]
\item Conducted market research and stakeholder interviews to define business requirements for fleet optimization.
\item Created business case with ROI analysis for fuel efficiency and CO2 tracking features.
\item Documented functional requirements, user stories, and acceptance criteria.
\item Coordinated between business stakeholders and development team throughout implementation.
\end{itemize}

\subsection*{E-commerce Platform (SmrtMart.com)}
\textbf{End-to-End Business \& Technical Design}
\begin{itemize}[noitemsep]
\item Analyzed e-commerce market requirements and defined product specifications.
\item Designed business processes for order management, inventory, and payment flows.
\item Created system architecture documentation aligning technical solutions with business objectives.
\item Live platform demonstrating ability to deliver complete business solutions: \href{https://www.smrtmart.com}{smrtmart.com}
\end{itemize}

\subsection*{JobHunter Automation Platform}
\textbf{Business Process Automation}
\begin{itemize}[noitemsep]
\item Identified inefficiencies in job application process and designed automated solution.
\item Created requirements documentation and process flow diagrams.
\item Demo: https://jobs.bluehawana.com
\end{itemize}

\section*{Education}

\textbf{University of Gothenburg} | \textbf{Master's in International Business \& Trade} | 2016-2019\\
\textit{Core: Business analysis, strategic planning, international commerce, financial analysis, stakeholder management}\\
\textit{This business education provides deep understanding of commercial operations and business value creation.}

\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Focus: Cloud architecture, system design, databases, APIs - technical foundation for IT analysis}

\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textit{Focus: Enterprise integration, system architecture, data modeling - IT systems knowledge}

\section*{Why I Bridge IT \& Business}

\textbf{Unique Background:} Master's in International Business combined with two IT degrees gives me the rare ability to understand both business strategy and technical implementation details.

\textbf{Translation Capability:} I can speak the language of both business executives and technical developers, ensuring requirements are correctly understood and solutions deliver business value.

\textbf{Hands-on IT Knowledge:} Unlike pure business analysts, I have actually built systems (databases, APIs, cloud infrastructure), giving me deep understanding of technical feasibility and constraints.

\textbf{Global Communication:} Fluent in English, Mandarin Chinese, and Swedish - essential for multinational stakeholder collaboration.

\section*{Certifications \& Professional Tools}

\textbf{Cloud Certifications:} AWS Solutions Architect Associate (2022) | AWS Developer Associate (2022) | Microsoft Azure Fundamentals (2022)

\textbf{Business Intelligence \& Analytics:} Microsoft Power BI (Advanced - data modeling, DAX, dashboards) | Tableau (data visualization, interactive dashboards) | Excel (Advanced - pivot tables, VLOOKUP, macros, financial modeling)

\textbf{Business Analysis \& Modeling Tools:} Microsoft Visio (process flows, BPMN, system diagrams) | Miro (collaborative workshops) | JIRA \& Confluence (requirements management) | SQL (data analysis, queries) | Microsoft 365 Suite (SharePoint, Teams, Project)

\end{document}
