\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\pagestyle{empty}

\definecolor{titlecolor}{RGB}{0,102,204}

\hypersetup{
    colorlinks=true,
    urlcolor=titlecolor
}

\begin{document}

\begin{flushleft}
\textbf{Harvad (Hongzhi) Li}\\
Gothenburg, Sweden\\
\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com}\\
+46 72 838 4299\\
\href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}
\end{flushleft}

\vspace{12pt}

January 30, 2026

\vspace{12pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Senior Android Developer position at Tech Company. With 6+ years of software development experience specializing in Android and React Native applications, combined with my unique ability to bridge cultural and business-technical gaps, I am confident I would be a valuable addition to your team.

\textbf{Technical Excellence with Real-World Impact}

My Android development expertise spans native Kotlin/Java applications and cross-platform React Native solutions. At ECARX (Geely Automotive), I developed Android-based automotive infotainment systems tested on Polestar 4 physical emulators. My personal projects demonstrate deep technical skills:

\begin{itemize}
\item \textbf{CarAI Assistant}: AI voice assistant for Android Auto with LLM integration and custom wake-word detection
\item \textbf{CarTV Player}: Customized Android Auto media player with enhanced controls and voice commands
\item \textbf{Gothenburg Taxi Pooling}: React Native app with real-time geolocation and Spring Boot backend
\item \textbf{Enterprise Info App}: Cross-platform React Native/Expo solution with offline-first architecture
\end{itemize}

All projects have been rigorously tested on physical devices, Polestar 4 emulator, and Firebase Test Lab, ensuring production-ready quality.

\textbf{Bridging Gaps: My Unique Value Proposition}

What sets me apart is my ability to bridge multiple gaps that often challenge international tech companies:

\textbf{1. Cultural Bridge (Chinese-Swedish-English):} As a native Chinese speaker with fluent English and Swedish B2, I excel at facilitating communication between Asian headquarters and European teams. At ECARX, I successfully bridged communication between Chinese management and Swedish developers, ensuring smooth project delivery across 4 global offices.

\textbf{2. Business-IT Bridge:} With a Master's in International Business combined with deep technical expertise, I translate complex business requirements into technical solutions. At Senior Material Europe AB, I worked directly with business stakeholders to understand their needs and delivered technical solutions that drove business value.

\textbf{3. Technical Bridge (Frontend-Backend-Mobile):} My full-stack background enables me to understand the entire application ecosystem. At Pembio and CollabMaker, I developed React Native mobile apps while collaborating seamlessly with backend teams, ensuring smooth API integration and optimal user experience.

\textbf{Proven Soft Skills \& Work Ethic}

My colleagues and managers consistently highlight my:

\begin{itemize}
\item \textbf{Communication Excellence}: Clear, proactive communication across technical and non-technical stakeholders
\item \textbf{Problem-Solving Mindset}: Creative solutions to complex technical and interpersonal challenges
\item \textbf{Team Collaboration}: Positive attitude, strong team player, and natural charisma that energizes teams
\item \textbf{Self-Management}: Proven ability to work independently and deliver results under pressure
\item \textbf{Adaptability}: Successfully worked in diverse environments from startups to large automotive corporations
\item \textbf{Results-Driven}: Track record of completing projects on time with high quality standards
\end{itemize}

At Senior Material Europe AB, I demonstrated exceptional ability to work with international teams, managing complex stakeholder relationships while delivering technical solutions. My entrepreneurial background (Hong Yan AB, 8+ years) further proves my self-motivation, business acumen, and ability to see projects through from concept to completion.

\textbf{Why I'm Excited About This Opportunity}

I am particularly drawn to Tech Company because of the opportunity to contribute my unique combination of technical expertise and cross-cultural communication skills. In today's global tech landscape, the ability to bridge cultural and business-technical gaps is increasingly valuable. I am confident that my trilingual capabilities, technical skills, and proven track record of making things happen would make me an asset to your team.

I am eager to bring my Android development expertise, soft skills, and cultural bridge capabilities to Tech Company. I would welcome the opportunity to discuss how my background and skills align with your team's needs.

Thank you for considering my application. I look forward to the possibility of contributing to Tech Company's success.

\vspace{12pt}

Best regards,

\vspace{12pt}

\textbf{Harvad (Hongzhi) Li}

\vspace{6pt}

\textit{P.S. All my Android projects are available on GitHub (\href{https://github.com/bluehawana}{github.com/bluehawana}) with detailed documentation and testing reports. I would be happy to demonstrate any of them during an interview.}

\end{document}
