\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,51,102}

% Section formatting
\titleformat{\section}{\large\bfseries\raggedright\color{black}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty} % no page number

% Recipient address
{\color{darkblue}
Essity\\
Cloud DevOps Engineering Team\\
Munich, Germany}

\vspace{30pt}

% Opening
\textbf{Dear Hiring Manager,}

\vspace{8pt}

I am writing to express my strong interest in the Cloud DevOps Engineer position at Essity. With over 5 years of experience in cloud technologies, DevOps, and site reliability engineering, I am excited to contribute to Essity's mission of sustainable hygiene and health solutions.

At ECARX, I led our cloud infrastructure transformation, architecting a hybrid approach that balanced cost and performance. Our 4-node Dell HPC cluster delivers 259\% better performance than Azure's HB120rs\_v3 flagship VM while reducing costs by 40\%. This required deep systems engineering—CPU affinity optimization, memory tuning, and NUMA-aware scheduling—instrumented with Prometheus, Grafana, and Alertmanager for SLO-driven capacity planning. Your requirement for Azure DevOps CI/CD multi-staging pipelines aligns perfectly with my experience implementing dev, staging, and production environments with automated testing, security scanning, and zero-downtime deployments. My software development background in Python, C\#, and Go enables me to bridge development and operations effectively, while my AWS certifications and current Azure Developer Associate (AZ-204) preparation demonstrate my commitment to cloud excellence.

What particularly resonates with me about Essity is your commitment to sustainability and the "Business Ambition for 1.5 Degrees" initiative. I am passionate about leveraging technology to create positive environmental impact, and I would be honored to contribute my DevOps and cloud expertise to help Essity achieve climate neutrality by 2050 while delivering high-quality hygiene and health solutions with maximum resource efficiency.

I am eager to bring my DevOps expertise, cloud architecture knowledge, and passion for sustainable technology to Essity's team in Munich. Thank you for considering my application. I look forward to the opportunity to discuss how I can contribute to Essity's continued success.

\vspace{10pt}

% Closing
Sincerely,

\vspace{15pt}

Harvad (Hongzhi) Li

\vspace{20pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}

\vspace{4pt}

{\color{darkblue}
Ebbe Lieberathsgatan 27\\
412 65 Göteborg, Sweden\\
hongzhili01@gmail.com | 0728 384 299\\
LinkedIn: \href{https://www.linkedin.com/in/hzl/}{linkedin.com/in/hzl} | GitHub: \href{https://github.com/bluehawana}{github.com/bluehawana}}

\end{document}
