\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

{\color{linkedinblue}
\noindent Ahlsell \\
Lars Andersen \\
lars.andersen@ahlsell.com \\
Årstaängsvägen 11 \\
117 43 Stockholm, Sweden
}

\vspace{2cm}

Hej Lars,

\vspace{0.5cm}
I am excited to apply for the Fullstack Developer position at Ahlsell. As a fullstack developer specializing in the Microsoft ecosystem (C\#/.NET + React + Azure), I am drawn to the opportunity to build scalable e-commerce solutions that drive real business value.

My experience spans the entire Microsoft stack. At ECARX, I manage Azure cloud infrastructure, implementing CI/CD pipelines with Azure DevOps and GitHub Actions. I recently led a Kubernetes migration that achieved 65\% cost reduction while tripling performance—demonstrating my focus on both technical excellence and business impact through cloud resource optimization.

What sets me apart is my ability to bridge technical and business worlds. My Master's in International Business, combined with hands-on development experience, means I understand how technology decisions affect the bottom line. This cross-cultural communication ability, honed working with teams across 4 global offices, enables me to collaborate effectively in international environments—particularly valuable for companies like Ahlsell operating across Nordic markets.

Beyond my professional work, I'm passionate about building practical systems that solve real business demands. I built SmrtMart.com as a hobby project—a live e-commerce platform with Stripe payment integration, microservices architecture, and Kubernetes deployment. It's one thing to work on enterprise systems; it's another to build and maintain your own production e-commerce platform. I also created the AI Math Grader and Invoice Handling System—both solving real business demands with smooth, AI-integrated solutions. This hands-on experience gives me deep empathy for technical challenges and demonstrates my ability to architect IT/data-driven solutions that address actual business needs.

I'm fluent in English and Mandarin Chinese, with Swedish B2 proficiency. I would love to discuss how my fullstack expertise, Azure cloud management experience, and business-IT integration mindset can contribute to Ahlsell's continued success.

Sincerely, \\
Harvad (Hongzhi) Li

\vspace{2cm}

{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

\noindent Ebbe Lieberathsgatan 27 \\
412 65 Göteborg, Sweden

\end{document}
