\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=0.6in}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\itemsep}{0pt}
\pagestyle{empty}

\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}
\titleformat{\section}{\Large\bfseries\color{linkedinblue}}{}{0em}{}[\vspace{-4pt}\titlerule\vspace{2pt}]
\titleformat{\subsection}{\large\bfseries}{}{0em}{}[\vspace{-2pt}]

\begin{document}
\pagestyle{empty}

\begin{center}
{\Large \textbf{COMPANY\_NAME}}\\[4pt]
{\Large \textbf{JOB\_TITLE}}\\[4pt]
{\Large \textbf{Gothenburg, Sweden}}\\[8pt]
\textcolor{linkedinblue}{\href{mailto:hongzhili01@gmail.com}{hongzhili01@gmail.com} | \href{tel:0728384299}{0728 384 299} | \href{https://www.linkedin.com/in/hzl/}{LinkedIn} | \href{https://github.com/bluehawana}{GitHub}}
\end{center}
\vspace{8pt}

\section*{Profile Summary}
Fullstack Developer with 5+ years building scalable e-commerce and B2B platforms using C\#/.NET backend and React frontend. Strong expertise in microservices architecture, event-driven patterns, and distributed systems. Proven experience with Kubernetes, Azure, Grafana, and OpenTelemetry for observability and performance optimization. Passionate about automated testing, CI/CD pipelines, and delivering maintainable, high-quality solutions. Currently at ECARX managing infrastructure for automotive platforms with global reach.

\section*{Core Technical Skills}
\begin{itemize}[noitemsep]
\item \textbf{Backend:} C\#/.NET Core, ASP.NET, RESTful APIs, Microservices, Event-Driven Architecture
\item \textbf{Frontend:} React, Vue.js, JavaScript, TypeScript, HTML5, CSS3, Responsive Design
\item \textbf{Infrastructure:} Kubernetes, Azure (AKS, App Services, Functions), Terraform (IaC), Docker
\item \textbf{Observability \& Monitoring:} Grafana, Prometheus, OpenTelemetry, ELK Stack, Performance Tuning
\item \textbf{CI/CD:} GitHub Actions, Azure DevOps, Jenkins, Automated Testing Pipelines
\item \textbf{Databases:} SQL Server, PostgreSQL, MongoDB, Redis, Entity Framework Core
\item \textbf{E-commerce \& B2B:} Payment Systems, Order Management, Inventory Tracking, CMS Integration
\item \textbf{Distributed Systems:} Scalability, Resilience, Load Balancing, Caching Strategies
\item \textbf{Testing:} xUnit, NUnit, Jest, TDD, Integration Testing, Automated Test Suites
\item \textbf{Agile:} Scrum, Kanban, Sprint Planning, Cross-functional Collaboration
\item \textbf{Languages:} Fluent in English and Mandarin Chinese; Swedish (B2 level)
\end{itemize}

\section*{Professional Experience}

\subsection*{ECARX (Geely Automotive) | IT/Infrastructure Specialist}
\textit{October 2024 - Present | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Leading globally distributed infrastructure optimization for automotive technology platforms, managing Kubernetes clusters and Azure cloud resources across 4 international offices.
\item Implemented comprehensive observability stack using Grafana, Prometheus, and Loki, enabling proactive monitoring and 25\% reduction in incident response time.
\item Architected and deployed CI/CD pipelines with GitHub Actions and Azure DevOps, achieving automated testing coverage and zero-downtime deployments for microservices.
\item Migrated critical workloads from Azure AKS to on-premise Kubernetes, resulting in 65\% cost reduction and 259\% performance improvement through systematic optimization.
\item Providing 24/7 production support for distributed systems, ensuring high availability and rapid incident resolution for mission-critical automotive services.
\item Collaborated with cross-functional teams to design scalable, event-driven architectures supporting real-time data processing and integration patterns.
\end{itemize}

\subsection*{Synteda | C\# .NET Fullstack Developer \& Integration Specialist}
\textit{August 2023 - September 2024 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Developed comprehensive talent management platform using C\# .NET Core backend and React frontend, hosted on Azure with microservices architecture.
\item Built RESTful APIs and implemented event-driven patterns for scalable application architecture, handling complex business workflows and data synchronization.
\item Integrated SQL Server and MongoDB databases with optimized query performance, implementing caching strategies for improved response times.
\item Established automated CI/CD pipelines via Azure DevOps, ensuring reliable high-frequency releases with comprehensive test coverage.
\item Collaborated with stakeholders to translate business requirements into technical solutions, delivering user-friendly and efficient B2B platform features.
\end{itemize}

\subsection*{IT-Högskolan | Backend Developer (Part-time)}
\textit{January 2023 - May 2023 | Gothenburg, Sweden}
\begin{itemize}[noitemsep]
\item Migrated "Omstallningsstod.se" adult education platform using Spring Boot backend services with microservices architecture.
\item Developed RESTful APIs for frontend integration and implemented secure data handling with automated testing.
\item Collaborated with UI/UX designers to ensure seamless frontend-backend integration and optimal user experience.
\end{itemize}

\subsection*{Senior Material (Europe) AB | Fullstack Platform Architect}
\textit{January 2022 - December 2022 | Eskilstuna, Sweden}
\begin{itemize}[noitemsep]
\item Led digital transformation of manufacturing platforms in lithium-ion battery sector, migrating monolithic applications to containerized microservices.
\item Architected scalable backend solutions with Spring Boot and integrated modern React frontends for real-time data visualization.
\item Implemented distributed systems patterns for performance optimization and data integrity during critical technical transitions.
\end{itemize}

\section*{E-commerce \& Fullstack Projects}

\subsection*{Fleet Management Dashboard}
\textit{2024 -- Present} \\
\textbf{.NET 8, React 18, SQL Server 2022, Azure, Docker, GitHub Actions}
\begin{itemize}[noitemsep]
\item Built intelligent fleet tracking platform using US DOT data to optimize fuel efficiency and CO2 tracking for sustainable transport operations.
\item Implemented microservices architecture with event-driven patterns for real-time data processing and predictive maintenance analytics.
\item Leveraged Azure App Service and Docker for scalable hosting, with fully automated CI/CD pipelines via GitHub Actions.
\item Integrated Grafana dashboards for operational monitoring and performance metrics visualization.
\end{itemize}

\subsection*{SmrtMart E-commerce Platform}
\textit{April 2024 -- Present} \\
\textbf{Go, Next.js, PostgreSQL, Microservices, Stripe API, Kubernetes}
\begin{itemize}[noitemsep]
\item Fullstack e-commerce platform with microservices architecture for scalable order processing and inventory management.
\item Integrated Stripe payment systems and hybrid PostgreSQL/MongoDB storage for high transaction volumes.
\item Deployed on Kubernetes with Terraform IaC, implementing load balancing and auto-scaling for resilient systems.
\item Live demo: \href{https://www.smrtmart.com}{www.smrtmart.com}
\end{itemize}

\subsection*{AI Math Grader Ecosystem}
\textit{2025 -- Present} \\
\textbf{C\# .NET 8, React, AI/LLM (Gemini/OpenAI), Python, PDF Export}
\begin{itemize}[noitemsep]
\item Developed full-stack automated grading system for K-12 math, providing instant pedagogical feedback using advanced LLM integration.
\item Architected modular API layer with C\# .NET for AI-driven feedback loops, ensuring low-latency processing and high accuracy.
\item Built React frontend with responsive design and integrated white-label PDF export functionality for accessible result sharing.
\end{itemize}

\subsection*{JobHunter Automation Platform}
\textit{July 2025 -- Present} \\
\textbf{Python, TypeScript, React, Gmail REST API, LinkedIn API}
\begin{itemize}[noitemsep]
\item Automated job hunting pipeline integrating Gmail search, job scraping, and resume customization with NLP techniques.
\item Built React-based dashboard for application tracking and management with real-time updates.
\item Demo: https://jobs.bluehawana.com
\end{itemize}

\section*{Additional Full-Stack Projects}

\subsection*{Weather\_Anywhere.CLOUD}
\textit{2024 -- Present} \\
\textbf{Spring Boot, React, Alibaba Cloud, MySQL, RESTful APIs}
\begin{itemize}[noitemsep]
\item Developed weather visualization platform with React frontend consuming RESTful APIs from Spring Boot backend.
\item Deployed on Alibaba Cloud ECS with ApsaraDB RDS, implementing caching strategies for cost-effective cloud usage.
\item Architected responsive UI with real-time data updates and interactive weather maps.
\item Demo: \href{https://weather.bluehawana.com}{weather.bluehawana.com}
\end{itemize}

\subsection*{AndroidAuto\_AI\_Bot}
\textit{2025} \\
\textbf{Android, Kotlin, TypeScript, LLM APIs, Real-time Processing}
\begin{itemize}[noitemsep]
\item Built AI-powered voice assistant for automotive use with native Android frontend and cloud-based LLM integration.
\item Designed RESTful APIs for real-time AI processing with Edge TTS voice synthesis integration.
\item Implemented performance-optimized UI compliant with automotive safety standards for distraction-free interaction.
\end{itemize}

\subsection*{Invoice\_Handling\_System}
\textit{2025} \\
\textbf{C\# .NET, React, Azure, AI/OCR Integration}
\begin{itemize}[noitemsep]
\item Developed automated invoice processing system using OCR and AI for Swedish businesses (fakturahantering).
\item Built fullstack solution with C\# .NET backend for document processing and React frontend for invoice management.
\item Integrated Azure AI services for intelligent data extraction, reducing manual data entry by 80\%.
\end{itemize}

\section*{Business \& Technical Leadership}

\textbf{Cross-Cultural Communication:} Fluent in English, Mandarin Chinese, and Swedish (B2), with experience working across 4 global offices (Gothenburg, London, Stuttgart, San Diego).

\textbf{IT-Business Integration:} Master's in International Business \& Trade combined with technical expertise, enabling translation of business requirements into scalable technical solutions.

\textbf{Problem-Solving Mindset:} Track record of solving business demands with IT solutions: SmrtMart (e-commerce), AI Math Grader (education tech), Invoice Handling (business automation), JobHunter (recruitment automation).

\section*{Education \& Certifications}

\textbf{IT Högskolan} | Bachelor's in .NET Cloud Development | 2021-2023\\
\textit{Focus: C\# backend development, cloud architecture, microservices, Azure, databases}

\textbf{Mölndal Campus} | Bachelor's in Java Integration | 2019-2021\\
\textit{Focus: Enterprise integration, Spring Framework, RESTful APIs, SQL databases}

\textbf{University of Gothenburg} | Master's in International Business \& Trade | 2016-2019\\
\textit{Focus: Business analysis, international commerce, B2B operations}

\textbf{Cloud Certifications:} AWS Certified Solutions Architect - Associate (Aug 2022), AWS Certified Developer - Associate (Nov 2022), Microsoft Certified: Azure Fundamentals (Jun 2022)

\vspace{20pt}
\begin{flushright}
\textit{Harvad (Hongzhi) Li}\\
\textit{Gårdsvägen 9, 431 38 Mölndal, Sweden}
\end{flushright}

\end{document}
