\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\definecolor{linkedinblue}{RGB}{0,119,181}
\hypersetup{colorlinks=true, linkcolor=linkedinblue, urlcolor=linkedinblue}

\begin{document}

{\color{linkedinblue}
\noindent [Company Name] \\
Hiring Manager \\
[Contact Email] \\
[Address] \\
[City], Sweden
}

\vspace{2cm}

Hej,

\vspace{0.5cm}

I am excited to apply for the [Position] position at [Company Name]. As a DevOps engineer with a unique background bridging business and technology, I bring not just technical expertise, but the ability to understand business needs and translate them into data-driven infrastructure solutions.

My experience spans cloud infrastructure and international collaboration. At ECARX, I manage infrastructure across 4 global offices (Gothenburg, London, Stuttgart, San Diego), working daily with Swedish, British, German, and American teams. I led an Azure-to-Kubernetes migration that achieved 65\% cost reduction while tripling performance—demonstrating my focus on both technical excellence and business impact through strategic optimization.

What sets me apart is my ability to bridge technical and business worlds. My Master's in International Business, combined with hands-on infrastructure experience, means I see beyond the technology stack—I understand how infrastructure decisions affect operational costs, team productivity, and business agility. This cross-cultural communication ability and business-IT integration mindset enable me to spot real-world problems and solve them with data-driven solutions.

Beyond my professional work, I build practical AI-powered systems. I created the AI Math Grader—a K-12 grading system that addresses real teachers' needs for instant, pedagogical feedback. I also developed an Invoice Handling System using AI to streamline financial workflows. Both projects came from observing real business demands and solving them with smooth, AI-integrated solutions. This demonstrates my ability to identify pain points and architect practical technical solutions.

I'm fluent in English and Mandarin Chinese, with Swedish B2 proficiency, enabling seamless collaboration in multicultural environments. I would love to discuss how my cloud infrastructure expertise, cross-cultural communication skills, and business-IT integration mindset can contribute to [Company Name]'s continued success.

\vspace{0.5cm}

Sincerely, \\
Harvad (Hongzhi) Li

\vspace{2cm}

{\color{linkedinblue}\hrule height 0.5pt}

\vspace{0.3cm}

\noindent Gårdsvägen 9 \\
431 38 Mölndal, Sweden \\
hongzhili01@gmail.com \\
+46 72 838 4299

\end{document}
