\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{rgb}{0.0, 0.4, 0.8}

% Remove paragraph indentation
\setlength{\parindent}{0pt}

\begin{document}
\pagestyle{empty}

{\color{darkblue}Omnimodular AB\\
Product Engineer (AI \& SaaS)\\
Sweden}

\vspace{40pt}

Dear Hiring Team,

\vspace{10pt}

I'm writing to apply for the Product Engineer position at Omnimodular. As someone who has built AI-powered products from scratch - including an Android Auto voice assistant that outperforms Google Assistant and a conversational toy platform serving 1000+ users - I'm excited about the opportunity to be "The Stitcher" who brings your Post-Template technology to life.

\textbf{Why I'm the Right "Stitcher":} I live at the intersection of AI, product, and engineering. My JobHunter project demonstrates this perfectly: I integrated MiniMax M2 AI to achieve 95\% accurate role detection, built the full React/TypeScript/Python stack, and deployed it to production - all while obsessing over user experience and reliability. This is exactly the "stitching" mindset Omnimodular needs.

\textbf{AI Integration Expertise:} I don't just call APIs - I architect systems that make AI reliable for critical use cases. In SagaToy.com, I implemented RAG strategies for context-aware conversations and built guardrails ensuring child-safe content. For CarBot, I designed fallback logic for safety-critical automotive scenarios. I understand that "prompt engineering is software development in natural language" and that 99.7\% accuracy requires engineering discipline, not just model selection.

\textbf{Full-Stack Product Builder:} I've shipped production applications using your exact tech stack: React/TypeScript frontends, Python backends, and OpenAI API integration. At Ecarx, I reduced cloud costs 45\% while improving CI/CD efficiency 25\% - proving I care about both user experience and operational excellence. I don't wait for Jira tickets; I understand business goals and figure out the best technical path forward.

\textbf{AI Coding Tools Mastery:} I'm proficient with all major AI development tools - Cursor, Claude Code, Copilot, Qwen, MiniMax, Kiro, Antigravity. I leverage these tools daily to accelerate development while maintaining code quality. This meta-skill of "AI-assisted development" is crucial for a team building the future of AI-powered fintech.

\textbf{Fearless \& Product-Oriented:} I've worked alongside technical experts at Geely Automotive across 4 global offices. I'm not intimidated by PhDs in mathematics - I'm energized by learning from them. I care deeply about user friction, latency, and time-to-value because I've experienced the pain of slow, clunky interfaces in my own products.

\textbf{Why Omnimodular?} Your "Post-Template" vision resonates deeply. In building JobHunter, I experienced the limitations of rigid templates firsthand. The future isn't about filling in blanks - it's about systems that understand context and deliver accurate results. I want to work on problems that matter, with a team that values engineering excellence over "code monkeying."

I'm based in Gothenburg with Swedish permanent residence and available immediately for either part-time or full-time arrangements. I'd love to discuss how my experience building AI products can help Omnimodular automate millions of transactions and eliminate thousands of hours of manual work.

Thank you for considering my application. I look forward to the opportunity to be your "Stitcher."

\vspace{10pt}

Best regards,

Harvad Lee

\vspace{40pt}

{\color{darkblue}\rule{\linewidth}{0.6pt}}

\vspace{4pt}

{\color{darkblue}Ebbe Lieberathsgatan 27\\
412 65 Göteborg\\
hongzhili01@gmail.com\\
+46 72 838 4299\\
\href{https://sagatoy.com}{sagatoy.com} | \href{https://github.com/bluehawana}{github.com/bluehawana}\\
December 29, 2025}

\end{document}
